---
title: "ZWE_MIHPSA_Phase_1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load libraries}
library(tidyverse)
library(tidyr)
library(data.table)
library(magrittr)
library(ggplot2)
library(devtools)
devtools::install_github("BershteynLab/EMODAnalyzeR")

```

```{r Functions}

# Confidence interval functions
lower_ci <- function(mean, se, n, conf_level = 0.95){
  lower_ci <- mean - qt(1 - ((1 - conf_level) / 2), n - 1) * se
}
upper_ci <- function(mean, se, n, conf_level = 0.95){
  upper_ci <- mean + qt(1 - ((1 - conf_level) / 2), n - 1) * se
}
```

# ZWE MIHPSA Phase 1
The purpose of this notebook is to generate the phase 1 requirements for MIHPSA Zimbabwe

# Load data

```{r}

```

# Flow Variables

## HIV incidence in 15-49 year olds

```{r}
# males
p1 <- sim.results %>% 
  filter(Gender == 0, Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  mutate(incidence = 100 * incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_M1549_M = mean(incidence), 
            HIVIncid_M1549_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_M1549_95LL = lower_ci(HIVIncid_M1549_M, HIVIncid_M1549_se, 99, conf_level = .95),
    HIVIncid_M1549_95UL = upper_ci(HIVIncid_M1549_M, HIVIncid_M1549_se, 99, conf_level = .95)
    )

# females
p2 <- sim.results %>% 
  filter(Gender == 1, Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  mutate(incidence = 100 * incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_F1549_M = mean(incidence), 
            HIVIncid_F1549_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_F1549_95LL = lower_ci(HIVIncid_F1549_M, HIVIncid_F1549_se, 99, conf_level = .95),
    HIVIncid_F1549_95UL = upper_ci(HIVIncid_F1549_M, HIVIncid_F1549_se, 99, conf_level = .95)
    )

# all
p3  <- sim.results %>% 
  filter(Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_A1549_M = mean(incidence), 
            HIVIncid_A1549_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_A1549_95LL = lower_ci(HIVIncid_A1549_M, HIVIncid_A1549_se, 99, conf_level = .95),
    HIVIncid_A1549_95UL = upper_ci(HIVIncid_A1549_M, HIVIncid_A1549_se, 99, conf_level = .95)
    )

inc.1549.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  mutate(Year = floor(Year)) 
```

## New HIV infections

NHIVInf_M1549_M
NHIVInf_M1549_95LL
NHIVInf_M1549_95UL
NHIVInf_F1549_M
NHIVInf_F1549_95LL
NHIVInf_F1549_95UL
NHIVInf_A1549_M
NHIVInf_A1549_95LL
NHIVInf_A1549_95UL

## AIDS Deaths
AIDSDeaths_M1599_M
AIDSDeaths_M1599_95LL
AIDSDeaths_M1599_95UL
AIDSDeaths_F1599_M
AIDSDeaths_F1599_95LL
AIDSDeaths_F1599_95UL
AIDSDeaths_A1599_M
AIDSDeaths_A1599_95LL
AIDSDeaths_A1599_95UL
AIDSDeaths_A014_M
AIDSDeaths_A014_95LL
AIDSDeaths_A014_95UL

## Total Deaths
TOTDeaths_M1599_M
TOTDeaths_M1599_95LL
TOTDeaths_M1599_95UL
TOTDeaths_F1599_M
TOTDeaths_F1599_95LL
TOTDeaths_F1599_95UL
TOTDeaths_A014_M
TOTDeaths_A014_95LL
TOTDeaths_A014_95UL

## Total HIV tests performed in adults

TOTTests_M1599_M
TOTTests_M1599_95LL
TOTTests_M1599_95UL
TOTTests_F1599_M
TOTTests_F1599_95LL
TOTTests_F1599_95UL
TOTTests_A1599_M
TOTTests_A1599_95LL
TOTTests_A1599_95UL

## Proportion of adult hiv tests with positive results

PosRate_A1599_M
PosRate_A1599_95LL
PosRate_A1599_95UL

## Number VMMC operations

NVMMC_M1549_M
NVMMC_M014_M

## HIV incidence again

```{r}
# HIV incidence all ages
p1 <- sim.results %>% 
  filter(Gender == 1, Age >=15, Age < 25) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_A099_M = mean(incidence), 
            HIVIncid_A099_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_A099_95LL = lower_ci(HIVIncid_A099_M, HIVIncid_A099_se, 99, conf_level = .95),
    HIVIncid_A099_95UL = upper_ci(HIVIncid_A099_M, HIVIncid_A099_se, 99, conf_level = .95)
    )

# HIV incidence in 15-24 year olds
p2 <- sim.results %>% 
  filter(Gender == 0, Age >=15, Age < 25) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_M1524_M = mean(incidence), 
            HIVIncid_M1524_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_M1524_95LL = lower_ci(HIVIncid_M1524_M, HIVIncid_M1524_se, 99, conf_level = .95),
    HIVIncid_M1524_95UL = upper_ci(HIVIncid_M1524_M, HIVIncid_M1524_se, 99, conf_level = .95)
    )

p3 <- sim.results %>% 
  filter(Gender == 1, Age >=15, Age < 25) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_F1524_M = mean(incidence), 
            HIVIncid_F1524_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_F1524_95LL = lower_ci(HIVIncid_F1524_M, HIVIncid_F1524_se, 99, conf_level = .95),
    HIVIncid_F1524_95UL = upper_ci(HIVIncid_F1524_M, HIVIncid_F1524_se, 99, conf_level = .95)
    )

# HIV incidence in 25-49 year olds
p4 <- sim.results %>% 
  filter(Gender == 0, Age >=25, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_M2549_M = mean(incidence), 
            HIVIncid_M2549_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_M2549_95LL = lower_ci(HIVIncid_M2549_M, HIVIncid_M2549_se, 99, conf_level = .95),
    HIVIncid_M2549_95UL = upper_ci(HIVIncid_M2549_M, HIVIncid_M2549_se, 99, conf_level = .95)
    )

p5 <- sim.results %>% 
  filter(Gender == 1, Age >=25, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_F2549_M = mean(incidence), 
            HIVIncid_F2549_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_F2549_95LL = lower_ci(HIVIncid_F2549_M, HIVIncid_F2549_se, 99, conf_level = .95),
    HIVIncid_F2549_95UL = upper_ci(HIVIncid_F2549_M, HIVIncid_F2549_se, 99, conf_level = .95)
    )

inc.other.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  mutate(Year = floor(Year)) 
```

## HIV new HIV infections in 15-24 year olds

NHIVInf_M1524_M
NHIVInf_M1524_95LL
NHIVInf_M1524_95UL
NHIVInf_F1524_M
NHIVInf_F1524_95LL
NHIVInf_F1524_95UL

## HIV new HIV infections in 25-49 year olds

NHIVInf_M2549_M
NHIVInf_M2549_95LL
NHIVInf_M2549_95UL
NHIVInf_F2549_M
NHIVInf_F2549_95LL
NHIVInf_F2549_95UL

# Stock Variables

## HIV prevalence in age group 15-49

HIVprev_M1549_M
HIVprev_M1549_95LL
HIVprev_M1549_95UL
HIVprev_F1549_M
HIVprev_F1549_95LL
HIVprev_F1549_95UL
HIVprev_A1549_M
HIVprev_A1549_95LL
HIVprev_A1549_95UL

## ART coverage children and adults

P_onART_HIVM1599_M
P_onART_HIVM1599_95LL
P_onART_HIVM1599_95UL
P_onART_HIVF1599_M
P_onART_HIVF1599_95LL
P_onART_HIVF1599_95UL
P_onART_HIVA014_M
P_onART_HIVA014_95LL
P_onART_HIVA014_95UL
P_onART_HIVA099_M
P_onART_HIVA099_95LL
P_onART_HIVA099_95UL

## Number of children and adults on ART

NOnART_M1599_M
NOnART_M1599_95LL
NOnART_M1599_95UL
NOnART_F1599_M
NOnART_F1599_95LL
NOnART_F1599_95UL
NOnART_A1524_M
NOnART_A1524_95LL
NOnART_A1524_95UL
NOnART_A099_M
NOnART_A099_95LL
NOnART_A099_95UL

## % of men age 15-49 who have been circumcised

CIRC_PREV_M1549_M
CIRC_PREV_M1549_95LL
CIRC_PREV_M1549_95UL

## % HIV+ individuals who have been diagnosed

P_DIAG_M1599_M
P_DIAG_M1599_95LL
P_DIAG_M1599_95UL
P_DIAG_F1599_M
P_DIAG_F1599_95LL
P_DIAG_F1599_95UL
P_DIAG_A014_M
P_DIAG_A014_95LL
P_DIAG_A014_95UL
P_DIAG_A099_M
P_DIAG_A099_95LL
P_DIAG_A099_95UL

## % VLS

P_VLS_onARTA1599_M
P_VLS_onARTA1599_95LL
P_VLS_onARTA1599_95UL

(This one is easy; it's 92% everywhere)

## Population size
NAlive_A1599_M
NAlive_A01599_95LL
NAlive_A01599_95UL
NAlive_A1549_M
NAlive_A01549_95LL
NAlive_A01549_95UL
NAlive_M1599_M
NAlive_M1599_95LL
NAlive_M1599_95UL
NAlive_F1599_M
NAlive_F1599_95LL
NAlive_F1599_95UL
NAlive_A014_M
NAlive_A014_95LL
NAlive_A014_95UL
NAlive_A099_M
NAlive_A099_95LL
NAlive_A099_95UL

## % of individuals diagnosed with HIV on ART

P_onART_DiagM1599_M
P_onART_DiagM1599_95LL
P_onART_DiagM1599_95UL
P_onART_DiagF1599_M
P_onART_DiagF1599_95LL
P_onART_DiagF1599_95UL
P_onART_DiagA014_M
P_onART_DiagA014_95LL
P_onART_DiagA014_95UL
P_onART_DiagA099_M
P_onART_DiagA099_95LL
P_onART_DiagA099_95UL

## HIV prevalence in age group 15-24

HIVprev_M1524_M
HIVprev_M1524_95LL
HIVprev_M1524_95UL
HIVprev_F1524_M
HIVprev_F1524_95LL
HIVprev_F1524_95UL

## HIV prevalence in age group 25-49

HIVprev_M2549_M
HIVprev_M2549_95LL
HIVprev_M2549_95UL
HIVprev_F2549_M
HIVprev_F2549_95LL
HIVprev_F2549_95UL

## HIV prevalence among fsw

HIVprev_FSW1599_M
HIVprev_FSW1599_95LL
HIVprev_FSW1599_95UL

# Wrangle output

inc.1549.summary


inc.other.summary
