---
title: "ZWE_MIHPSA_Phase_2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load libraries}
library(tidyverse)
library(tidyr)
library(data.table)
library(magrittr)
library(ggplot2)
library(devtools)
devtools::install_github("BershteynLab/EMODAnalyzeR")

```

```{r Functions}

# Confidence interval functions
lower_ci <- function(mean, se, n, conf_level = 0.95){
  lower_ci <- mean - qt(1 - ((1 - conf_level) / 2), n - 1) * se/sqrt(n)
}
upper_ci <- function(mean, se, n, conf_level = 0.95){
  upper_ci <- mean + qt(1 - ((1 - conf_level) / 2), n - 1) * se/sqrt(n)
}
```


# Postprocessing Zimbabwe Model

The purpose of this notebook is to perform postprocessing and analysis of the initial Phase 2 scenarios for the Zimbabwe MIHPSA collaboration.

There are two sets of outputs to analyze:

* "Essential Scenario" - baseline, with no PrEP
* Essential Scenario + PrEP - adding 45k PrEP initiations per year after 2020 or so.


# Read in Simulation Data

## Read in Essential Scenario Simulation

```{r}
res_path = "/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/ZWE_phase2/Baseline-campaign_ZWE_MIHPSA_2023_noprep-noprep/ReportHIVByAgeAndGender"
sim.results.base <- EMODAnalyzeR::read.simulation.results(
  results_path  = res_path,
  scenario_name = 'prep',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed", 
                        "Infected.CD4.Under.200..Not.On.ART.", "Infected.CD4.200.To.349..Not.On.ART.",
                        "Infected.CD4.350.To.499..Not.On.ART.", "Infected.CD4.500.Plus..Not.On.ART.",
                        "ReceivePrEP_HIGH"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.Risk"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

```

## Read in PrEP Scenario Simulation Runs
```{r Read in PrEP Scenario Simulation Runs}

res_path = "/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/ZWE_phase2/Baseline-campaign_ZWE_MIHPSA_2023-prep/ReportHIVByAgeAndGender"

sim.results.prep <- EMODAnalyzeR::read.simulation.results(
  results_path  = res_path,
  scenario_name = 'prep',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed", 
                        "Infected.CD4.Under.200..Not.On.ART.", "Infected.CD4.200.To.349..Not.On.ART.",
                        "Infected.CD4.350.To.499..Not.On.ART.", "Infected.CD4.500.Plus..Not.On.ART.",
                        "ReceivePrEP_HIGH"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.Risk"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)


```

## Scale by population scaling factor
```{r Scale by Population Scaling Factor}
CENSUS_YEAR = 2010
ZWE_CENSUS_POP = 12696893 # WPP data

sim.results.pop.scaling <- sim.results.base %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = ZWE_CENSUS_POP/total.pop)

sim.results.base <- sim.results.base %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )


sim.results.pop.scaling <- sim.results.prep %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = ZWE_CENSUS_POP/total.pop)

sim.results.prep <- sim.results.prep %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )



```

# Compare results to calibration targets

## Prevalence plots

```{r Prevalence calibration targets}
zwe.phia = data.frame(
  Year = c(2016, 2016),
  Gender = c("Male", "Female"),
  mean.prev= c(12, 16),
  lower = c(11.1, 15.3),
  upper = c(12.8,16.8)
)
zwe.dhs = data.frame(
  Year = c(2006, 2010, 2015, 2006, 2010, 2015),
  Gender = c("Male", "Male", "Male", "Female", "Female", "Female"),
  mean.prev = c(14.5, 12.3, 10.5, 21.1, 17.7, 16.7),
  lower = c(13.2, 11.3, 9.5, 19.6, 16.6, 15.5),
  upper = c(15.9, 13.3, 11.5, 22.6, 18.8, 17.8)
)
 
prev.target <- rbind(zwe.phia, zwe.dhs) %>% arrange(Year, Gender)
```

```{r Prevalence}
p <- EMODAnalyzeR::emodplot.prevalence(
      #sim.results.base %>% filter(Age >= 15, Age < 50),
      sim.results.prep %>% filter(Age >= 15, Age < 50),
  date.start = 1990,
  date.end = 2020
)

p +
  geom_errorbar(data = prev.target,
             mapping = aes(x = Year, ymin = lower/100, ymax = upper/100)) + 
  facet_wrap(~ Gender, ncol=2)
```

```{r Prevalence by Age}

# Read in the calibration targets data
prev.target <- read_csv("/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/Analysis/zwe_age_prevalence_data.csv")

# Convenient relabels of age bins
prev.target$Age = factor(prev.target$AgeBin, 
                         levels = c("[0:5)", "[5:10)", "[10:15)", "[15:20)", "[20:25)", "[25:30)", "[30:35)", "[35:40)", "[40:45)", "[45:50)", "[50:55)", "[55:60)", "[60:65)"),
                         labels = c(1:13)
                         )

prev.target$Year.label = factor(prev.target$Year, 
                          levels = c(2006.0, 2011.0, 2015.0, 2016),
                          labels = c( "2006 (DHS)","2011 (DHS)", "2015 (DHS)", "2016 (PHIA)"))

#head(prev.target)

```

```{r}
age_bins = c(0,5,10,15,20,25,30,35,40,45,50,55,60,65)
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

subset_years = c(2006.0, 2011.0, 2015.0, 2016)

data <- sim.results.prep %>% 
  select(Year, Age, Gender, sim.id, Infected, Population) %>% 
  filter(Year %in% subset_years) %>% 
  mutate(AgeBin = cut(Age, breaks = age_bins, right = FALSE)) %>% 
  group_by(Year, AgeBin, Gender, sim.id) %>% 
  summarize(Infected = sum(Infected), Population = sum(Population)) %>% ungroup() %>% 
  mutate(Prevalence = Infected/Population)

data.mean <-  data %>% 
  group_by(Year, AgeBin, Gender) %>% 
  summarize(Prevalence = mean(Prevalence), .groups = 'keep')  %>% 
  ungroup() %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))
data.mean$AgeBin_index = factor(data.mean$AgeBin,labels = 1:length(age_labels))

ggplot() + 
  geom_point(data.mean, mapping = aes(x = AgeBin_index, y = Prevalence), color = 'blue') + 
  geom_point(data = prev.target, 
             mapping = aes(x = Age, y = Prevalence)) + 
  geom_errorbar(data = prev.target,
                mapping = aes(x = Age, ymin = lower, ymax = upper)) +
  facet_grid(cols = vars(Gender), rows = vars(Year)) 

```

## ART Plots

```{r}
xl.path = "/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/Data/calibration_ingest_form_ZWE_2022-07-15.xlsm"
obs.onart.sheet <- EMODAnalyzeR::read.ingest.sheet(xl.path, sheet = 'Obs-OnART')
```


```{r}
data <- sim.results.prep %>% 
    group_by(Year, Gender, sim.id, scenario_name) %>% 
    summarize(On_ART = sum(On_ART*pop.scaling.factor), 
              Population = sum(Population*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup()

p <- EMODAnalyzeR::emodplot.by_gender(data, 1990, 2040, 'On_ART', title="ART") 

p + 
  geom_point(data = obs.onart.sheet %>% filter(Province == "All", AgeBin == '[15:100)') %>% 
    group_by(Year, Gender) %>% 
    summarize(OnART = sum(OnART), .groups = 'keep'),
    mapping= aes(x = Year, y = OnART))
```


# Extract Results for MIHPSA

## HIV Incidence

### PrEP

```{r Incidence - prep}
# Males 15-49
p1 <- sim.results.prep %>% 
  filter(Gender == 0, Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  mutate(incidence = 100 * incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_M1549_M = mean(incidence), 
            HIVIncid_M1549_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_M1549_95LL = lower_ci(HIVIncid_M1549_M, HIVIncid_M1549_se, 99, conf_level = .95),
    HIVIncid_M1549_95UL = upper_ci(HIVIncid_M1549_M, HIVIncid_M1549_se, 99, conf_level = .95)
    )

# Females 15-49
p2 <- sim.results.prep %>% 
  filter(Gender == 1, Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  mutate(incidence = 100 * incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_F1549_M = mean(incidence), 
            HIVIncid_F1549_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_F1549_95LL = lower_ci(HIVIncid_F1549_M, HIVIncid_F1549_se, 99, conf_level = .95),
    HIVIncid_F1549_95UL = upper_ci(HIVIncid_F1549_M, HIVIncid_F1549_se, 99, conf_level = .95)
    )

# Adults 15-49
p3 <- sim.results.prep %>% 
  filter(Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_A1549_M = mean(incidence), 
            HIVIncid_A1549_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_A1549_95LL = lower_ci(HIVIncid_A1549_M, HIVIncid_A1549_se, 99, conf_level = .95),
    HIVIncid_A1549_95UL = upper_ci(HIVIncid_A1549_M, HIVIncid_A1549_se, 99, conf_level = .95)
    )

# Females 15-24
p4 <- sim.results.prep %>% 
  filter(Gender == 1, Age >=15, Age < 25) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_F1524_M = mean(incidence), 
            HIVIncid_F1524_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_F1524_95LL = lower_ci(HIVIncid_F1524_M, HIVIncid_F1524_se, 99, conf_level = .95),
    HIVIncid_F1524_95UL = upper_ci(HIVIncid_F1524_M, HIVIncid_F1524_se, 99, conf_level = .95)
    )

# FSW ages >15
p5 <- sim.results.prep %>% 
  filter(Gender == 1, Age >= 15, IP_Key.Risk == "HIGH") %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_FSW1599_M = mean(incidence), 
            HIVIncid_FSW1599_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_FSW1599_95LL = lower_ci(HIVIncid_FSW1599_M, HIVIncid_FSW1599_se, 99, conf_level = .95),
    HIVIncid_FSW1599_95UL = upper_ci(HIVIncid_FSW1599_M, HIVIncid_FSW1599_se, 99, conf_level = .95)
    )

inc.prep.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  mutate(Year = floor(Year)) 

# inc.prep.summary %>% 
#   pivot_longer(-Year) %>% 
#   pivot_wider(names_from = Year, values_from = value)


ggplot(data = inc.prep.summary) + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_M1549_M), color = 'blue') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_F1549_M), color = 'green') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_A1549_M), color = 'purple') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_F1524_M), color = 'black') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_FSW1599_M), color = 'red')

```


### Essential

```{r Incidence}
# Males 15-49
p1 <- sim.results.base %>% 
  filter(Gender == 0, Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  mutate(incidence = 100 * incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_M1549_M = mean(incidence), 
            HIVIncid_M1549_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_M1549_95LL = lower_ci(HIVIncid_M1549_M, HIVIncid_M1549_se, 99, conf_level = .95),
    HIVIncid_M1549_95UL = upper_ci(HIVIncid_M1549_M, HIVIncid_M1549_se, 99, conf_level = .95)
    )

# Females 15-49
p2 <- sim.results.base %>% 
  filter(Gender == 1, Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  mutate(incidence = 100 * incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_F1549_M = mean(incidence), 
            HIVIncid_F1549_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_F1549_95LL = lower_ci(HIVIncid_F1549_M, HIVIncid_F1549_se, 99, conf_level = .95),
    HIVIncid_F1549_95UL = upper_ci(HIVIncid_F1549_M, HIVIncid_F1549_se, 99, conf_level = .95)
    )

# Adults 15-49
p3 <- sim.results.base %>% 
  filter(Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_A1549_M = mean(incidence), 
            HIVIncid_A1549_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_A1549_95LL = lower_ci(HIVIncid_A1549_M, HIVIncid_A1549_se, 99, conf_level = .95),
    HIVIncid_A1549_95UL = upper_ci(HIVIncid_A1549_M, HIVIncid_A1549_se, 99, conf_level = .95)
    )

# Females 15-24
p4 <- sim.results.base %>% 
  filter(Gender == 1, Age >=15, Age < 25) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_F1524_M = mean(incidence), 
            HIVIncid_F1524_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_F1524_95LL = lower_ci(HIVIncid_F1524_M, HIVIncid_F1524_se, 99, conf_level = .95),
    HIVIncid_F1524_95UL = upper_ci(HIVIncid_F1524_M, HIVIncid_F1524_se, 99, conf_level = .95)
    )

# FSW ages >15
p5 <- sim.results.base %>% 
  filter(Gender == 1, Age >= 15, IP_Key.Risk == "HIGH") %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_FSW1599_M = mean(incidence), 
            HIVIncid_FSW1599_se = mean_se(incidence)$y, .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_FSW1599_95LL = lower_ci(HIVIncid_FSW1599_M, HIVIncid_FSW1599_se, 99, conf_level = .95),
    HIVIncid_FSW1599_95UL = upper_ci(HIVIncid_FSW1599_M, HIVIncid_FSW1599_se, 99, conf_level = .95)
    )

inc.base.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  mutate(Year = floor(Year)) 

# inc.base.summary %>% 
#   pivot_longer(-Year) %>% 
#   pivot_wider(names_from = Year, values_from = value)


ggplot(data = inc.base.summary) + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_M1549_M), color = 'blue') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_F1549_M), color = 'green') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_A1549_M), color = 'purple') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_F1524_M), color = 'black') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_FSW1599_M), color = 'red')

```

## Oral PrEP for AGYW

### PrEP

```{r}
# Number of AGYW who used oral TDF in the last year
p1 <- sim.results.prep %>% 
  filter(Gender == 1, Age >=15, Age < 25) %>% 
  dplyr::select(Year, sim.id, ReceivePrEP_HIGH, pop.scaling.factor) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NTDFPrEP_F1524_M = sum(ReceivePrEP_HIGH*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NTDFPrEP_F1524_M = mean(NTDFPrEP_F1524_M), .groups = 'keep') %>% 
  ungroup()

# Number of FSWs who used oral TDF in the last year
p2 <- sim.results.prep %>% 
  filter(Gender == 1, Age >=15, IP_Key.Risk == 'HIGH') %>% 
  dplyr::select(Year, sim.id, ReceivePrEP_HIGH, pop.scaling.factor) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NTDFPrEP_FSW1599_M = sum(ReceivePrEP_HIGH*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NTDFPrEP_FSW1599_M = mean(NTDFPrEP_FSW1599_M), .groups = 'keep') %>% 
  ungroup()

# Number AGYW at elevated risk
p3 <- sim.results.prep %>% 
  filter(Gender == 1, Age >= 15, Age <25, IP_Key.Risk == 'HIGH') %>% 
  dplyr::select(Year, sim.id, Population, pop.scaling.factor) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NAlive_ElevRiskF1524_M = sum(Population*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_ElevRiskF1524_M = mean(NAlive_ElevRiskF1524_M), .groups = 'keep') %>% 
  ungroup()

# % AGYW at high risk on prep
p4 <- sim.results.prep %>% 
  filter(Gender == 1, Age >= 15, Age <25, IP_Key.Risk == 'HIGH') %>% 
  dplyr::select(Year, sim.id, Population, ReceivePrEP_HIGH) %>% 
  group_by(Year, sim.id) %>% 
  summarize(onprep = sum(ReceivePrEP_HIGH), 
            pop = sum(Population), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(P_TDFPrEP_ElevRiskF1524_M = 100*mean(onprep/pop), .groups = 'keep') %>% 
  ungroup()

prep.prep.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  mutate(Year = floor(Year)) 

ggplot(data = prep.prep.summary) + 
  geom_line(mapping = aes(x = Year, y = NTDFPrEP_F1524_M), color = 'green') + 
  geom_line(mapping = aes(x = Year, y = NTDFPrEP_FSW1599_M), color = 'purple') + 
  geom_line(mapping = aes(x = Year, y = NAlive_ElevRiskF1524_M), color = 'black')
  #geom_line(mapping = aes(x = Year, y = P_TDFPrEP_ElevRiskF1524_M), color = 'red')
```

### Essential

```{r}
# Number of AGYW who used oral TDF in the last year
p1 <- sim.results.base %>% 
  filter(Gender == 1, Age >=15, Age < 25) %>% 
  dplyr::select(Year, sim.id, ReceivePrEP_HIGH, pop.scaling.factor) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NTDFPrEP_F1524_M = sum(ReceivePrEP_HIGH*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NTDFPrEP_F1524_M = mean(NTDFPrEP_F1524_M), .groups = 'keep') %>% 
  ungroup()

# Number of FSWs who used oral TDF in the last year
p2 <- sim.results.base %>% 
  filter(Gender == 1, Age >=15, IP_Key.Risk == 'HIGH') %>% 
  dplyr::select(Year, sim.id, ReceivePrEP_HIGH, pop.scaling.factor) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NTDFPrEP_FSW1599_M = sum(ReceivePrEP_HIGH*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NTDFPrEP_FSW1599_M = mean(NTDFPrEP_FSW1599_M), .groups = 'keep') %>% 
  ungroup()

# Number AGYW at elevated risk
p3 <- sim.results.base %>% 
  filter(Gender == 1, Age >= 15, Age <25, IP_Key.Risk == 'HIGH') %>% 
  dplyr::select(Year, sim.id, Population, pop.scaling.factor) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NAlive_ElevRiskF1524_M = sum(Population*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_ElevRiskF1524_M = mean(NAlive_ElevRiskF1524_M), .groups = 'keep') %>% 
  ungroup()

# % AGYW at high risk on prep
p4 <- sim.results.base %>% 
  filter(Gender == 1, Age >= 15, Age <25, IP_Key.Risk == 'HIGH') %>% 
  dplyr::select(Year, sim.id, Population, ReceivePrEP_HIGH) %>% 
  group_by(Year, sim.id) %>% 
  summarize(onprep = sum(ReceivePrEP_HIGH), 
            pop = sum(Population), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(P_TDFPrEP_ElevRiskF1524_M = 100*mean(onprep/pop), .groups = 'keep') %>% 
  ungroup()

prep.base.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  mutate(Year = floor(Year)) 

ggplot(data = prep.base.summary) + 
  geom_line(mapping = aes(x = Year, y = NTDFPrEP_F1524_M), color = 'green') + 
  geom_line(mapping = aes(x = Year, y = NTDFPrEP_FSW1599_M), color = 'purple') + 
  geom_line(mapping = aes(x = Year, y = NAlive_ElevRiskF1524_M), color = 'black')
  #geom_line(mapping = aes(x = Year, y = P_TDFPrEP_ElevRiskF1524_M), color = 'red')
```

## YLDs - current categories

Use the assumption that other people are using: that 1/8 of the people who have CD4 under 200 have CD4 under 50

### PrEP
```{r}
# check: how do we sum up the total number of infected people, or infected people on art

# sim.results.prep %>% 
#   filter(Year == 2010) %>% 
#   dplyr::select(Year, Population, Infected, On_ART, 
#                 Infected.CD4.Under.200..Not.On.ART., Infected.CD4.200.To.349..Not.On.ART.,
#                 Infected.CD4.350.To.499..Not.On.ART., Infected.CD4.500.Plus..Not.On.ART.
#                 ) %>% 
#   group_by(Year) %>% 
#   summarize(Population = sum(Population),
#             Infected = sum(Infected),
#             On_ART = sum(On_ART),
#             Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.),
#             Infected.CD4.200.To.349..Not.On.ART. = sum(Infected.CD4.200.To.349..Not.On.ART.),
#             Infected.CD4.350.To.499..Not.On.ART. = sum(Infected.CD4.350.To.499..Not.On.ART.),
#             Infected.CD4.500.Plus..Not.On.ART. = sum(Infected.CD4.500.Plus..Not.On.ART.),
#             .groups = 'keep') %>% 
#   pivot_longer( cols = c("Population", "Infected", "On_ART",
#                          "Infected.CD4.Under.200..Not.On.ART.",
#                          "Infected.CD4.200.To.349..Not.On.ART.",
#                          "Infected.CD4.350.To.499..Not.On.ART.",
#                          "Infected.CD4.500.Plus..Not.On.ART."))
```


```{r}
# Number of 15+ PLHIV not on treatment, with CD4 >= 500
# NHIV_A1599_NoART_CD4500pl_M
p1 <- sim.results.prep %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.500.Plus..Not.On.ART. = sum(Infected.CD4.500.Plus..Not.On.ART. * pop.scaling.factor), 
            .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD4500pl_M = mean(Infected.CD4.500.Plus..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 350 <= CD4 < 500
#NHIV_A1599_NoART_CD4350499_M
p2 <- sim.results.prep %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.350.To.499..Not.On.ART. = sum(Infected.CD4.350.To.499..Not.On.ART.* pop.scaling.factor ), 
            .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD4350499_M = mean(Infected.CD4.350.To.499..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 200 <= CD4 < 350
# NHIV_A1599_NoART_CD4200349_M
p3  <- sim.results.prep %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.200.To.349..Not.On.ART. = sum(Infected.CD4.200.To.349..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD4200349_M = mean(Infected.CD4.200.To.349..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 50 <= CD4 < 200
# NHIV_A1599_NoART_CD450199_M
p4a  <- sim.results.prep %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor)*7/8, .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD450199_M = mean(Infected.CD4.Under.200..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 0 <= CD4 < 50
# NHIV_A1599_NoART_CD4050_M
p4b  <- sim.results.prep %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor)/8, .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD4050_M = mean(Infected.CD4.Under.200..Not.On.ART.))


# Number of 0-14yo PLHIV not on treatment, with CD4 >= 500
# NHIV_A014_NoART_CD4500pl_M
p5 <- sim.results.prep %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.500.Plus..Not.On.ART. = sum(Infected.CD4.500.Plus..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD4500pl_M = mean(Infected.CD4.500.Plus..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 350 <= CD4 < 500
# NHIV_A014_NoART_CD4350499_M
p6 <- sim.results.prep %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.200.To.349..Not.On.ART. = sum(Infected.CD4.200.To.349..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD4350499_M = mean(Infected.CD4.200.To.349..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 200 <= CD4 < 350
# NHIV_A014_NoART_CD4200349_M
p7 <- sim.results.prep %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.350.To.499..Not.On.ART. = sum(Infected.CD4.350.To.499..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD4200349_M = mean(Infected.CD4.350.To.499..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 0 <= CD4 < 200
# NHIV_A014_NoART_CD450199_M
p8a <- sim.results.prep %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor)*7/8, .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD450199_M = mean(Infected.CD4.Under.200..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 0 <= CD4 < 200
# NHIV_A014_NoART_CD4050_M
p8b <- sim.results.prep %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor)/8, .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD4050_M = mean(Infected.CD4.Under.200..Not.On.ART.))

ylds.current.prep <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4a, by = 'Year') %>%
  merge(p4b, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  merge(p6, by = 'Year') %>%
  merge(p7, by = 'Year') %>%
  merge(p8a, by = 'Year') %>%
  merge(p8b, by = 'Year') %>%
  mutate(Year = floor(Year)) 
```

### Essential

```{r}
# Number of 15+ PLHIV not on treatment, with CD4 >= 500
# NHIV_A1599_NoART_CD4500pl_M
p1 <- sim.results.base %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.500.Plus..Not.On.ART. = sum(Infected.CD4.500.Plus..Not.On.ART. * pop.scaling.factor), 
            .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD4500pl_M = mean(Infected.CD4.500.Plus..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 350 <= CD4 < 500
#NHIV_A1599_NoART_CD4350499_M
p2 <- sim.results.base %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.350.To.499..Not.On.ART. = sum(Infected.CD4.350.To.499..Not.On.ART.* pop.scaling.factor ), 
            .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD4350499_M = mean(Infected.CD4.350.To.499..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 200 <= CD4 < 350
# NHIV_A1599_NoART_CD4200349_M
p3  <- sim.results.base %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.200.To.349..Not.On.ART. = sum(Infected.CD4.200.To.349..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD4200349_M = mean(Infected.CD4.200.To.349..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 0 <= CD4 < 200
# NHIV_A1599_NoART_CD450199_M
p4  <- sim.results.base %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD450199_M = mean(Infected.CD4.Under.200..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with CD4 >= 500
# NHIV_A014_NoART_CD4500pl_M
p5 <- sim.results.base %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.500.Plus..Not.On.ART. = sum(Infected.CD4.500.Plus..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD4500pl_M = mean(Infected.CD4.500.Plus..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 350 <= CD4 < 500
# NHIV_A014_NoART_CD4350499_M
p6 <- sim.results.base %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.200.To.349..Not.On.ART. = sum(Infected.CD4.200.To.349..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD4350499_M = mean(Infected.CD4.200.To.349..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 200 <= CD4 < 350
# NHIV_A014_NoART_CD4200349_M
p7 <- sim.results.base %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.350.To.499..Not.On.ART. = sum(Infected.CD4.350.To.499..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD4200349_M = mean(Infected.CD4.350.To.499..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 0 <= CD4 < 200
# NHIV_A014_NoART_CD450199_M
p8 <- sim.results.base %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD450199_M = mean(Infected.CD4.Under.200..Not.On.ART.))

ylds.current.base <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  merge(p6, by = 'Year') %>%
  merge(p7, by = 'Year') %>%
  merge(p8, by = 'Year') %>%
  mutate(Year = floor(Year)) 
```
## YLDs - new categories

```{r}
# Asymptomatic, Undiagnosed

# Asymptomatic, Diagnosed, not on ART

# Asymptomatic, Diagnosed, on ART

# Symptomatic, not AIDS

# Symptomatic, AIDS
```

## YLLs

For all individuals who died from HIV at age X, find the correct life expectancy for that individual
Then sum up the difference between the age of death and the life expectancy

```{r Load Life Expectancy Tables}

xl.path <- "/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/Analysis/YLL_Tables.xlsx"

le.table.undisc <- readxl::read_excel(xl.path, sheet = "Undiscounted", range = "A1:C93", col_names = TRUE)
colnames(le.table.undisc) <- c("Age", 1, 0)
le.table.undisc <- pivot_longer(
  le.table.undisc, 
  cols = c(`0`,`1`),
  names_to = c("Gender"),
  values_to = "YLL")
```


### PrEP


```{r}
# Future YLL incurred at calendar year of death for adults aged 15+

# aggregate up the number of HIV related deaths for each age group

data.yll <- sim.results.prep %>% 
  dplyr::select(Year, Age, Gender, Died_from_HIV, sim.id, pop.scaling.factor) %>% 
  group_by(Year, Gender, Age, sim.id) %>% 
  # count total number of people who have died from HIV, 
  # for each year, age, gender and simulation
  summarize(Died_from_HIV = sum(Died_from_HIV*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  # merge with YLL table
  merge(le.table.undisc, 
        by = c("Age", "Gender"))

yll.adults <- data.yll  %>%   
  # subset on adults
  filter(Age >= 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_A1599_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()


yll.children <- data.yll  %>%   
  # subset on children
  filter(Age < 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_A014_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()
  
discount.percent = .03
discount_start_year = 2024

yll.adults.disc <- data.yll  %>%   
  # subset on adults
  filter(Age >= 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # calculate discount factor
  mutate(discount.factor = case_when(Year <= 2024 ~ 1,
                                     Year > 2024 ~ (1 - discount.percent)^(Year - discount_start_year))) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs * discount.factor), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_3Disc_A1599_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()


yll.children.disc <- data.yll  %>%   
  # subset on adults
  filter(Age < 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # calculate discount factor
  mutate(discount.factor = case_when(Year <= 2024 ~ 1,
                                     Year > 2024 ~ (1 - discount.percent)^(Year - discount_start_year))) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs * discount.factor), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_3Disc_A014_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()


ylls.current.prep <- merge(yll.adults, yll.children, by = 'Year') %>% 
  merge(yll.adults.disc, by = 'Year') %>% 
  merge(yll.children.disc, by = 'Year')
```

### Essential

```{r}
# Future YLL incurred at calendar year of death for adults aged 15+

# aggregate up the number of HIV related deaths for each age group

data.yll.base <- sim.results.base %>% 
  dplyr::select(Year, Age, Gender, Died_from_HIV, sim.id, pop.scaling.factor) %>% 
  group_by(Year, Gender, Age, sim.id) %>% 
  # count total number of people who have died from HIV, 
  # for each year, age, gender and simulation
  summarize(Died_from_HIV = sum(Died_from_HIV*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  # merge with YLL table
  merge(le.table.undisc, 
        by = c("Age", "Gender"))

yll.adults <- data.yll.base  %>%   
  # subset on adults
  filter(Age >= 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_A1599_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()


yll.children <- data.yll.base  %>%   
  # subset on children
  filter(Age < 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_A014_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()
  
discount.percent = .03
discount_start_year = 2024

yll.adults.disc <- data.yll.base  %>%   
  # subset on adults
  filter(Age >= 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # calculate discount factor
  mutate(discount.factor = case_when(Year <= 2024 ~ 1,
                                     Year > 2024 ~ (1 - discount.percent)^(Year - discount_start_year))) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs * discount.factor), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_3Disc_A1599_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()


yll.children.disc <- data.yll.base  %>%   
  # subset on adults
  filter(Age < 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # calculate discount factor
  mutate(discount.factor = case_when(Year <= 2024 ~ 1,
                                     Year > 2024 ~ (1 - discount.percent)^(Year - discount_start_year))) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs * discount.factor), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_3Disc_A014_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()


ylls.current.base <- merge(yll.adults, yll.children, by = 'Year') %>% 
  merge(yll.adults.disc, by = 'Year') %>% 
  merge(yll.children.disc, by = 'Year')
```

# Write out results to form

### PrEP Scenario
```{r}
analysis.path <- "/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/Analysis/"

(inc.prep.summary)[c(-3, -7, -11, -15, -19)] %>% filter(Year >= 2022) %>% 
  merge(ylls.current.prep  %>% filter(Year >= 2022),
      by = "Year") %>% 
  merge(prep.prep.summary  %>% filter(Year >= 2022),
        by = "Year") %>% 
  write_csv(file = paste0(analysis.path, 'Template_FLOW_prep_scenario.csv'))

ylds.current.prep %>% filter(Year >= 2023) %>% 
  write_csv(file = paste0(analysis.path, 'Template_STOCK_prep_scenario.csv'))
```

### Essential Scenario
```{r}
analysis.path <- "/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/Analysis/"

(inc.base.summary)[c(-3, -7, -11, -15, -19)] %>% filter(Year >= 2022) %>% 
  merge(ylls.current.base  %>% filter(Year >= 2022),
      by = "Year") %>% 
  merge(prep.base.summary  %>% filter(Year >= 2022),
        by = "Year") %>% 
  write_csv(file = paste0(analysis.path, 'Template_FLOW_essential_scenario.csv'))

ylds.current.base %>% filter(Year >= 2023) %>% 
  write_csv(file = paste0(analysis.path, 'Template_STOCK_essential_scenario.csv'))
```

