---
title: "ZWE_phase_2"
output: html_document
date: "2024-10-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The purpose of this notebook will be for generating the Phase 2 results for MIHPSA Zimbabwe.

The reports take up a lot of memory, so I recommend loading them into memory one at a time (or in small batches).

After loading in the report, there will be a series of code blocks to execute in sequence which will extract the metrics we need.

## Scenarios list

* Minimal
* Status quo = minimal + Routine Testing + VMMC and Oral TDF in AGYW going up through 2072
* Minimal + VMMC in 15-49 years old
* Minimal + Oral TDF/FTC PrEP
  * AGYW
  * FSW
  * SD couples
  * Pregnant women
* Minimal + Dapirivine
  * AGYW
  * FSW
  * SD couples
  * Pregnant women
* Minimal + Injectable PrEP
  * AGYW
  * FSW
  * SD couples
  * Pregnant women
* Minimal + SBCC
* Minimal + condom mass media campaign

# Load libraries

```{r Load libraries}
library(tidyverse)
library(data.table)
library(magrittr)
library(devtools)
devtools::install_github("BershteynLab/EMODAnalyzeR")
```

```{r Functions}
# Confidence interval functions
lower_ci <- function(mean, se, n, conf_level = 0.95){
  lower_ci <- mean - qt(1 - ((1 - conf_level) / 2), n - 1) * se/sqrt(n)
}

upper_ci <- function(mean, se, n, conf_level = 0.95){
  upper_ci <- mean + qt(1 - ((1 - conf_level) / 2), n - 1) * se/sqrt(n)
}
```

# Import data

First, set the path to the simulation results and the scenario name

```{r}
experiment.path = ""

scenario.name = "" 

# Scenario names
c("minimal", "")
```

Then, load the data as needed

```{r}
sim.results.all <- EMODAnalyzeR::read.simulation.results.bigpurple(
  experiment_path = experiment.path,
  scenario_name = scenario.name,
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed", 
                        "Newly.Tested.Positive", "Newly.Tested.Negative",
                        "HIVPositiveHIVTest","HIVNegativeHIVTest",
                        "Needs_PMTCT_Diagnostic_Test","NewlySymptomatic",
                        "Infected.CD4.Under.200..Not.On.ART.", "Infected.CD4.200.To.349..Not.On.ART.",
                        "Infected.CD4.350.To.499..Not.On.ART.", "Infected.CD4.500.Plus..Not.On.ART.",
                        "ReceivePrEP_HIGH", "Program_VMMC", "GaveBirth"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.Risk", "IsCircumcised"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)
```

Apply population scale factor:
```{r}
nruns <- 250

CENSUS_YEAR = 2011
ZWE_CENSUS_POP = 12696893 # WPP data

sim.results.pop.scaling <- sim.results.all %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = ZWE_CENSUS_POP/total.pop)

sim.results.all <- sim.results.all %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )

```

# Flow Variables

## Births

## HIV Incidence

```{r}
# Males 15-49
p1 <- sim.results.all %>%
  filter(Gender == 0, Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, scenario_name, sim.id, incidence) %>% 
  mutate(incidence = 100 * incidence) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(HIVIncid_M1549_sd = sd(incidence),
            HIVIncid_M1549_M = mean(incidence), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_M1549_95LL = lower_ci(HIVIncid_M1549_M, HIVIncid_M1549_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVIncid_M1549_95UL = upper_ci(HIVIncid_M1549_M, HIVIncid_M1549_sd/sqrt(nruns), nruns, conf_level = .95)
    ) %>% select(-HIVIncid_M1549_sd)

# Females 15-49
p2 <- sim.results.all %>% 
  filter(Gender == 1, Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, scenario_name, sim.id, incidence) %>% 
  mutate(incidence = 100 * incidence) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(HIVIncid_F1549_sd = sd(incidence),
            HIVIncid_F1549_M = mean(incidence), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_F1549_95LL = lower_ci(HIVIncid_F1549_M, HIVIncid_F1549_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVIncid_F1549_95UL = upper_ci(HIVIncid_F1549_M, HIVIncid_F1549_sd/sqrt(nruns), nruns, conf_level = .95)
    ) %>% select(-HIVIncid_F1549_sd)

# Adults 15-49
p3 <- sim.results.all %>% 
  filter(Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, scenario_name, sim.id, incidence) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(HIVIncid_A1549_sd = sd(incidence),
            HIVIncid_A1549_M = mean(incidence), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_A1549_95LL = lower_ci(HIVIncid_A1549_M, HIVIncid_A1549_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVIncid_A1549_95UL = upper_ci(HIVIncid_A1549_M, HIVIncid_A1549_sd/sqrt(nruns), nruns, conf_level = .95)
    ) %>% select(-HIVIncid_A1549_sd)

# Females 15-24
p4 <- sim.results.all %>% 
  filter(Gender == 1, Age >=15, Age < 25) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, Gender, scenario_name, sim.id, incidence) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(HIVIncid_F1524_sd = sd(incidence), 
            HIVIncid_F1524_M = mean(incidence),  .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_F1524_95LL = lower_ci(HIVIncid_F1524_M, HIVIncid_F1524_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVIncid_F1524_95UL = upper_ci(HIVIncid_F1524_M, HIVIncid_F1524_sd/sqrt(nruns), nruns, conf_level = .95)
    ) %>% select(-HIVIncid_F1524_sd)

# FSW ages >15
p5 <- sim.results.all %>% 
  filter(Gender == 1, Age >= 15, IP_Key.Risk == "HIGH") %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, Gender, scenario_name, sim.id, incidence) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(HIVIncid_FSW1599_sd = sd(incidence),
            HIVIncid_FSW1599_M = mean(incidence),  .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_FSW1599_95LL = lower_ci(HIVIncid_FSW1599_M, HIVIncid_FSW1599_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVIncid_FSW1599_95UL = upper_ci(HIVIncid_FSW1599_M, HIVIncid_FSW1599_sd/sqrt(nruns), nruns, conf_level = .95)
    ) %>% select(-HIVIncid_FSW1599_sd)

inc.summary <- merge(p1, p2, by = c('Year', 'scenario_name')) %>% 
  merge(p3, by = c('Year', 'scenario_name')) %>% 
  merge(p4, by = c('Year', 'scenario_name')) %>% 
  merge(p5, by = c('Year', 'scenario_name')) %>% 
  mutate(Year = floor(Year) + 1.5)

# inc.prep.summary %>% 
#   pivot_longer(-Year) %>% 
#   pivot_wider(names_from = Year, values_from = value)

# ggplot(data = inc.summary) + 
#   geom_line(mapping = aes(x = Year, y = HIVIncid_M1549_M), color = 'blue') + 
#   geom_line(mapping = aes(x = Year, y = HIVIncid_F1549_M), color = 'green') + 
#   geom_line(mapping = aes(x = Year, y = HIVIncid_A1549_M), color = 'purple') + 
#   geom_line(mapping = aes(x = Year, y = HIVIncid_F1524_M), color = 'black') + 
#   geom_line(mapping = aes(x = Year, y = HIVIncid_FSW1599_M), color = 'red')
```
## New HIV Infections

```{r}
# NHIVInf_M1599_M
p1 <- sim.results.all %>% 
  filter(Year == floor(Year)) %>% 
  filter(Age >=15, Gender == 0) %>% 
  group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(pop = sum(Newly.Infected * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIVInf_M1599_M_sd = sd(pop), 
            NHIVInf_M1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIVInf_M1599_95LL = lower_ci(NHIVInf_M1599_M, NHIVInf_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIVInf_M1599_95UL = upper_ci(NHIVInf_M1599_M, NHIVInf_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIVInf_M1599_M_sd)

# NHIVInf_F1599_M
p2 <- sim.results.all %>% 
  filter(Year == floor(Year)) %>% 
  filter(Age >=15, Gender == 1) %>% 
  group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(pop = sum(Newly.Infected * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIVInf_F1599_M_sd = sd(pop), 
            NHIVInf_F1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIVInf_F1599_95LL = lower_ci(NHIVInf_F1599_M, NHIVInf_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIVInf_F1599_95UL = upper_ci(NHIVInf_F1599_M, NHIVInf_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIVInf_F1599_M_sd)

# NHIVInf_A014_M
p3 <- sim.results.all %>% 
  filter(Year == floor(Year)) %>% 
  filter(Age < 15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(pop = sum(Newly.Infected * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIVInf_A014_M_sd = sd(pop), 
            NHIVInf_A014_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIVInf_A014_95LL = lower_ci(NHIVInf_A014_M, NHIVInf_A014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIVInf_A014_95UL = upper_ci(NHIVInf_A014_M, NHIVInf_A014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIVInf_A014_M_sd)

# NHIVInf_M1549_M
p4 <- sim.results.all %>% 
  filter(Year == floor(Year)) %>% 
  filter(Age >=15, Age <50, Gender == 0) %>% 
  group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(pop = sum(Newly.Infected * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIVInf_M1549_M_sd = sd(pop), 
            NHIVInf_M1549_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIVInf_M1549_95LL = lower_ci(NHIVInf_M1549_M, NHIVInf_M1549_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIVInf_M1549_95UL = upper_ci(NHIVInf_M1549_M, NHIVInf_M1549_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIVInf_M1549_M_sd)

# NHIVInf_F1549_M
p5 <- sim.results.all %>% 
  filter(Year == floor(Year)) %>% 
  filter(Age >=15, Age <50, Gender == 1) %>% 
  group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(pop = sum(Newly.Infected * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIVInf_F1549_M_sd = sd(pop), 
            NHIVInf_F1549_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIVInf_F1549_95LL = lower_ci(NHIVInf_F1549_M, NHIVInf_F1549_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIVInf_F1549_95UL = upper_ci(NHIVInf_F1549_M, NHIVInf_F1549_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIVInf_F1549_M_sd)

# NHIVInf_A1549_M
p6 <- sim.results.all %>% 
  filter(Year == floor(Year)) %>% 
  filter(Age >=15, Age <50) %>% 
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(pop = sum(Newly.Infected * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIVInf_A1549_M_sd = sd(pop), 
            NHIVInf_A1549_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIVInf_A1549_95LL = lower_ci(NHIVInf_A1549_M, NHIVInf_A1549_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIVInf_A1549_95UL = upper_ci(NHIVInf_A1549_M, NHIVInf_A1549_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIVInf_A1549_M_sd)

# NHIVInf_M1524_M
p7 <- sim.results.all %>% 
  filter(Year == floor(Year)) %>% 
  filter(Age >=15, Age <24, Gender == 0) %>% 
  group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(pop = sum(Newly.Infected * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIVInf_M1524_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup()

# NHIVInf_F1524_M
p8 <- sim.results.all %>% 
  filter(Year == floor(Year)) %>% 
  filter(Age >=15, Age <24, Gender == 1) %>% 
  group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(pop = sum(Newly.Infected * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIVInf_F1524_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup()

# NHIVInf_M2549_M
p9 <- sim.results.all %>% 
  filter(Year == floor(Year)) %>% 
  filter(Age >=25, Age <50, Gender == 0) %>% 
  group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(pop = sum(Newly.Infected * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIVInf_M2549_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup()

# NHIVInf_F2549_M
p10 <- sim.results.all %>% 
  filter(Year == floor(Year)) %>% 
  filter(Age >=25, Age <50, Gender == 1) %>% 
  group_by(Year, Gender, scenario_name, sim.ix) %>% 
  summarize(pop = sum(Newly.Infected * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIVInf_F2549_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup()

NHIVInf.summary <- merge(p1, p2, by = c('Year', 'scenario_name')) %>% 
  merge(p3, by = c('Year', 'scenario_name')) %>% 
  merge(p4, by = c('Year', 'scenario_name')) %>% 
  merge(p5, by = c('Year', 'scenario_name')) %>%
  merge(p5, by = c('Year', 'scenario_name')) %>%
  merge(p6, by = c('Year', 'scenario_name')) %>%
  merge(p7, by = c('Year', 'scenario_name')) %>%
  merge(p8, by = c('Year', 'scenario_name')) %>%
  merge(p9, by = c('Year', 'scenario_name')) %>%
  merge(p10, by = c('Year', 'scenario_name')) %>%
  mutate(Year = floor(Year) + .5) 

NHIVInf.summary %>% ggplot() +
  geom_line(mapping = aes(x = Year, y = NHIVInf_F1599_M, color = scenario_name ))
```

## HIV Deaths

```{r}
#AIDSDeaths_M1599_M
p1 <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >=15, Gender == 0) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(AIDSDeaths_M1599_M = sum(Died_from_HIV * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(AIDSDeaths_M1599_M_sd = sd(AIDSDeaths_M1599_M), 
            AIDSDeaths_M1599_M = mean(AIDSDeaths_M1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    AIDSDeaths_M1599_95LL = lower_ci(AIDSDeaths_M1599_M, AIDSDeaths_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    AIDSDeaths_M1599_95UL = upper_ci(AIDSDeaths_M1599_M, AIDSDeaths_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-AIDSDeaths_M1599_M_sd)

# AIDSDeaths_F1599_M
p2 <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >=15, Gender == 1) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(AIDSDeaths_F1599_M = sum(Died_from_HIV * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(AIDSDeaths_F1599_M_sd = sd(AIDSDeaths_F1599_M), 
            AIDSDeaths_F1599_M = mean(AIDSDeaths_F1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    AIDSDeaths_F1599_95LL = lower_ci(AIDSDeaths_F1599_M, AIDSDeaths_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    AIDSDeaths_F1599_95UL = upper_ci(AIDSDeaths_F1599_M, AIDSDeaths_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-AIDSDeaths_F1599_M_sd)

# AIDSDeaths_A1599_M
p3 <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >=15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(AIDSDeaths_A1599_M = sum(Died_from_HIV * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(AIDSDeaths_A1599_M_sd = sd(AIDSDeaths_A1599_M), 
            AIDSDeaths_A1599_M = mean(AIDSDeaths_A1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    AIDSDeaths_M1599_95LL = lower_ci(AIDSDeaths_A1599_M, AIDSDeaths_A1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    AIDSDeaths_M1599_95UL = upper_ci(AIDSDeaths_A1599_M, AIDSDeaths_A1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-AIDSDeaths_A1599_M_sd)

# AIDSDeaths_A014_M
p4 <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age <15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(AIDSDeaths_A014_M = sum(Died_from_HIV * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(AIDSDeaths_A014_M_sd = sd(AIDSDeaths_A014_M), 
            AIDSDeaths_A014_M = mean(AIDSDeaths_A014_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    AIDSDeaths_M1599_95LL = lower_ci(AIDSDeaths_A014_M, AIDSDeaths_A014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    AIDSDeaths_M1599_95UL = upper_ci(AIDSDeaths_A014_M, AIDSDeaths_A014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-AIDSDeaths_A014_M_sd)

HIVDeaths.summary <- merge(p1, p2, by = c('Year', 'scenario_name')) %>% 
  merge(p3, by = c('Year', 'scenario_name')) %>% 
  merge(p4, by = c('Year', 'scenario_name')) %>% 
  mutate(Year = floor(Year)+.5) 

HIVDeaths.summary %>% ggplot() + 
  geom_line(mapping = aes(x = Year, y = AIDSDeaths_F1599_M, color = scenario_name ))
```


## Total Deaths

```{r}
# TOTDeaths_M1599_M
p1 <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >=15, Gender == 0) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(TOTDeaths_M1599_M = sum(Died * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(TOTDeaths_M1599_M_sd = sd(TOTDeaths_M1599_M), 
            TOTDeaths_M1599_M = mean(TOTDeaths_M1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    TOTDeaths_M1599_95LL = lower_ci(TOTDeaths_M1599_M, TOTDeaths_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    TOTDeaths_M1599_95UL = upper_ci(TOTDeaths_M1599_M, TOTDeaths_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-TOTDeaths_M1599_M_sd)

# TOTDeaths_F1599_M
p2 <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >=15, Gender == 1) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(TOTDeaths_F1599_M = sum(Died * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(TOTDeaths_F1599_M_sd = sd(TOTDeaths_F1599_M), 
            TOTDeaths_F1599_M = mean(TOTDeaths_F1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    TOTDeaths_F1599_95LL = lower_ci(TOTDeaths_F1599_M, TOTDeaths_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    TOTDeaths_F1599_95UL = upper_ci(TOTDeaths_F1599_M, TOTDeaths_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-TOTDeaths_F1599_M_sd)

# TOTDeaths_A014_M
p3 <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age <15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(TOTDeaths_A014_M = sum(Died * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(TOTDeaths_A014_M_sd = sd(TOTDeaths_A014_M), 
            TOTDeaths_A014_M = mean(TOTDeaths_A014_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    TOTDeaths_A014_95LL = lower_ci(TOTDeaths_A014_M, TOTDeaths_A014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    TOTDeaths_A014_95UL = upper_ci(TOTDeaths_A014_M, TOTDeaths_A014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-TOTDeaths_A014_M_sd)

TOTDeaths.summary <- merge(p1, p2, by = c('Year', 'scenario_name')) %>% 
  merge(p3, by = c('Year', 'scenario_name')) %>% 
  mutate(Year = floor(Year)+.5) 
```

## YLLs

For all individuals who died from HIV at age X, find the correct life expectancy for that individual
Then sum up the difference between the age of death and the life expectancy

```{r Load Life Expectancy Tables}

xl.path <- "/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/Analysis/YLL_Tables.xlsx"

le.table.undisc <- readxl::read_excel(xl.path, sheet = "Undiscounted", range = "A1:C93", col_names = TRUE)
colnames(le.table.undisc) <- c("Age", 1, 0)
le.table.undisc <- pivot_longer(
  le.table.undisc, 
  cols = c(`0`,`1`),
  names_to = c("Gender"),
  values_to = "YLL")
```

```{r}
data.yll.base <- sim.results.all %>% 
  dplyr::select(Year, Age, Gender, Died_from_HIV, scenario_name, sim.ix, pop.scaling.factor) %>% 
  group_by(Year, Gender, scenario_name, Age, sim.ix) %>% 
  # count total number of people who have died from HIV, 
  # for each year, age, gender and simulation
  summarize(Died_from_HIV = sum(Died_from_HIV*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  # merge with YLL table
  merge(le.table.undisc, 
        by = c("Age", "Gender"))

# YLL_AgeGenLifeExpect_A1599_M
yll.adults <- data.yll.base  %>%   
  # subset on adults
  filter(Age >= 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # sum YLLs across age/gender
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(total.YLLs = sum(total.YLLs), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year, scenario_name) %>%
  summarize(YLL_AgeGenLifeExpect_A1599_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()

# YLL_AgeGenLifeExpect_A014_M
yll.children <- data.yll.base  %>%   
  # subset on children
  filter(Age < 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # sum YLLs across age/gender
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(total.YLLs = sum(total.YLLs), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year, scenario_name) %>%
  summarize(YLL_AgeGenLifeExpect_A014_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()

discount.percent = .03
discount_start_year = 2024

# YLL_AgeGenLifeExpect_3Disc_A1599_M
yll.adults.disc <- data.yll.base  %>%   
  # subset on adults
  filter(Age >= 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # calculate discount factor
  mutate(discount.factor = case_when(Year <= 2024 ~ 1,
                                     Year > 2024 ~ (1 - discount.percent)^(Year - discount_start_year))) %>% 
  # sum YLLs across age/gender
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(total.YLLs = sum(total.YLLs * discount.factor), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year, scenario_name) %>%
  summarize(YLL_AgeGenLifeExpect_3Disc_A1599_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()

# YLL_AgeGenLifeExpect_3Disc_A014_M
yll.children.disc <- data.yll.base  %>%   
  # subset on adults
  filter(Age < 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # calculate discount factor
  mutate(discount.factor = case_when(Year <= 2024 ~ 1,
                                     Year > 2024 ~ (1 - discount.percent)^(Year - discount_start_year))) %>% 
  # sum YLLs across age/gender
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(total.YLLs = sum(total.YLLs * discount.factor), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year, scenario_name) %>%
  summarize(YLL_AgeGenLifeExpect_3Disc_A014_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()

yll.summary <- merge(yll.adults, yll.children, by = c("Year", "scenario_name")) %>% 
  merge(yll.adults.disc, by = c("Year", "scenario_name")) %>% 
  merge(yll.children.disc, by = c("Year", "scenario_name")) %>% 
  mutate(Year = floor(Year) + .5)
```

## Testing

```{r}
# Ntested_ANCPD_F1599_M
p0 <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >=15, Gender == 0) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(Ntested_ANCPD_F1599_M = sum(Needs_PMTCT_Diagnostic_Test * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(Ntested_ANCPD_F1599_M = mean(Ntested_ANCPD_F1599_M), 
            .groups = 'keep') %>% 
  ungroup()

# TOTTests_M1599_M
p1 <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >=15, Gender == 0) %>%
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(TOTTests_M1599_M = sum((Newly.Tested.Positive + Newly.Tested.Negative) * pop.scaling.factor), 
            .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(TOTTests_M1599_M_sd = sd(TOTTests_M1599_M), 
            TOTTests_M1599_M = mean(TOTTests_M1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    TOTTests_M1599_95LL = lower_ci(TOTTests_M1599_M, TOTTests_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    TOTTests_M1599_95UL = upper_ci(TOTTests_M1599_M, TOTTests_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-TOTTests_M1599_M_sd)

# TOTTests_F1599_M
p2 <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >=15, Gender == 1) %>%
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(TOTTests_F1599_M = sum((Newly.Tested.Positive + Newly.Tested.Negative) * pop.scaling.factor), 
            .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(TOTTests_F1599_M_sd = sd(TOTTests_F1599_M), 
            TOTTests_F1599_M = mean(TOTTests_F1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    TOTTests_F1599_95LL = lower_ci(TOTTests_F1599_M, TOTTests_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    TOTTests_F1599_95UL = upper_ci(TOTTests_F1599_M, TOTTests_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-TOTTests_F1599_M_sd)

# TOTTests_A1599_M
p3 <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >=15) %>%
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(TOTTests_A1599_M = sum((Newly.Tested.Positive + Newly.Tested.Negative) * pop.scaling.factor), 
            .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(TOTTests_A1599_M_sd = sd(TOTTests_A1599_M), 
            TOTTests_A1599_M = mean(TOTTests_A1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    TOTTests_A1599_95LL = lower_ci(TOTTests_A1599_M, TOTTests_A1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    TOTTests_A1599_95UL = upper_ci(TOTTests_A1599_M, TOTTests_A1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-TOTTests_A1599_M_sd)

# PosRate_M1599_M
p4  <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >= 15, Gender == 0) %>% 
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(Newly.Tested.Positive = sum( Newly.Tested.Positive * pop.scaling.factor),
            Newly.Tested.Negative = sum(Newly.Tested.Negative * pop.scaling.factor),
            .groups = 'keep') %>% 
  mutate(PosRate_M1599_M = Newly.Tested.Positive/(Newly.Tested.Positive + Newly.Tested.Negative)) %>%
  group_by(Year, scenario_name) %>% 
  summarize(PosRate_M1599_M_sd = sd(PosRate_M1599_M),
            PosRate_M1599_M = mean(PosRate_M1599_M),
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    PosRate_M1599_95LL = lower_ci(PosRate_M1599_M, PosRate_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    PosRate_M1599_95UL = upper_ci(PosRate_M1599_M, PosRate_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-PosRate_M1599_M_sd) %>% 
  ungroup()


# PosRate_F1599_M
p5  <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >= 15, Gender == 1) %>% 
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(Newly.Tested.Positive = sum( Newly.Tested.Positive * pop.scaling.factor),
            Newly.Tested.Negative = sum(Newly.Tested.Negative * pop.scaling.factor),
            .groups = 'keep') %>% 
  mutate(PosRate_F1599_M = Newly.Tested.Positive/(Newly.Tested.Positive + Newly.Tested.Negative)) %>%
  group_by(Year, scenario_name) %>% 
  summarize(PosRate_F1599_M_sd = sd(PosRate_F1599_M),
            PosRate_F1599_M = mean(PosRate_F1599_M),
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    PosRate_F1599_95LL = lower_ci(PosRate_F1599_M, PosRate_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    PosRate_F1599_95UL = upper_ci(PosRate_F1599_M, PosRate_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-PosRate_F1599_M_sd) %>% 
  ungroup()

# PosRate_A1599_M
p6  <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >= 15) %>% 
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(Newly.Tested.Positive = sum( Newly.Tested.Positive * pop.scaling.factor),
            Newly.Tested.Negative = sum(Newly.Tested.Negative * pop.scaling.factor),
            .groups = 'keep') %>% 
  mutate(PosRate_A1599_M = Newly.Tested.Positive/(Newly.Tested.Positive + Newly.Tested.Negative)) %>%
  group_by(Year, scenario_name) %>% 
  summarize(PosRate_A1599_sd = sd(PosRate_A1599_M),
            PosRate_A1599_M = mean(PosRate_A1599_M),
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    PosRate_A1599_95LL = lower_ci(PosRate_A1599_M, PosRate_A1599_sd/sqrt(nruns), nruns, conf_level = .95),
    PosRate_A1599_95UL = upper_ci(PosRate_A1599_M, PosRate_A1599_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-PosRate_A1599_sd) %>% 
  ungroup()

# PosRate_F1524_M
p7 <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >= 15, Age < 25, Gender == 1) %>% 
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(Newly.Tested.Positive = sum( Newly.Tested.Positive * pop.scaling.factor),
            Newly.Tested.Negative = sum(Newly.Tested.Negative * pop.scaling.factor),
            .groups = 'keep') %>% 
  mutate(PosRate_F1524_M = Newly.Tested.Positive/(Newly.Tested.Positive + Newly.Tested.Negative)) %>%
  group_by(Year, scenario_name) %>% 
  summarize(PosRate_F1524_M = mean(PosRate_F1524_M),
            .groups = 'keep') %>% 
  ungroup()

# PosRate_FSW1599_M
p8 <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >= 15, Gender == 1, IP_Key.Risk == "HIGH") %>% 
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(Newly.Tested.Positive = sum( Newly.Tested.Positive * pop.scaling.factor),
            Newly.Tested.Negative = sum(Newly.Tested.Negative * pop.scaling.factor),
            .groups = 'keep') %>% 
  mutate(PosRate_FSW1599_M = Newly.Tested.Positive/(Newly.Tested.Positive + Newly.Tested.Negative)) %>%
  group_by(Year, scenario_name) %>% 
  summarize(PosRate_FSW1599_M = mean(PosRate_FSW1599_M),
            .groups = 'keep') %>% 
  ungroup()

Testing.summary <- merge(p1, p2, by = c("Year", "scenario_name")) %>% 
  merge(p3, by = c("Year", "scenario_name")) %>% 
  merge(p4, by = c("Year", "scenario_name")) %>% 
  merge(p5, by = c("Year", "scenario_name")) %>% 
  merge(p6, by = c("Year", "scenario_name")) %>% 
  merge(p7, by = c("Year", "scenario_name")) %>% 
  merge(p8, by = c("Year", "scenario_name")) %>% 
  mutate(Year = floor(Year) + .5)
```

## Number of VMMC
```{r}
# NVMMC_M1549_M
VMMC.summary <- sim.results.all %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >=15, Gender == 0) %>%
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(NVMMC_M1549_M = sum(Program_VMMC * pop.scaling.factor), 
            .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NVMMC_M1549_M = mean(NVMMC_M1549_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(Year = Year + .5)

VMMC.summary %>% ggplot() + 
  geom_point(mapping = aes(x = Year, y = NVMMC_M1549_M, color = scenario_name))
```

## PrEP received

This will depend on the exact scenario that we're in.

For TDF, simply count the number of PrEP initiations.
Once we get to writing out, however, I will need to retitle the PrEP initiation column

```{r}
### PrEP for AGYW
#NCABPrEP_F1524_M
p1.prep.agyw <- sim.results.all %>% 
  mutate(Year = ceiling(Year) + .5) %>% 
  filter(Age >=15, Age < 25, Gender == 1) %>%
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(PrEP_F1524_M = sum(ReceivePrEP_HIGH * pop.scaling.factor), 
            .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(PrEP_F1524_M = mean(PrEP_F1524_M), 
            .groups = 'keep') %>% 
  ungroup()

## PrEP for FSW
# NCABPrEP_FSW1599_M
p2.prep.fsw <- sim.results.all %>% 
  mutate(Year = ceiling(Year) + .5) %>% 
  filter(Age >=15, Age < 25, Gender == 1) %>%
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(PrEP_FSW1599_M = sum(ReceivePrEP_HIGH * pop.scaling.factor), 
            .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(PrEP_FSW1599_M = mean(PrEP_FSW1599_M), 
            .groups = 'keep') %>% 
  ungroup()

## PrEP for SD couples
# NCABPrEP_SDCA1599_M
p3.prep.sd <- sim.results.all %>% 
  mutate(Year = ceiling(Year) + .5) %>% 
  filter(Age >=15) %>%
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(PrEP_SDCA1599_M = sum(ReceivePrEP_HIGH * pop.scaling.factor), 
            .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(PrEP_SDCA1599_M = mean(PrEP_SDCA1599_M), 
            .groups = 'keep') %>% 
  ungroup()

## PReP for pregnant women
# NCABPrEP_pregbfF1549_M
p4.prep.plw <- sim.results.all %>% 
  mutate(Year = ceiling(Year) + .5) %>% 
  filter(Age >=15, Age < 50, Gender == 1) %>%
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(PrEP_pregbfF1549_M = sum(ReceivePrEP_HIGH * pop.scaling.factor), 
            .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(PrEP_pregbfF1549_M = mean(PrEP_pregbfF1549_M), 
            .groups = 'keep') %>% 
  ungroup()
```

### Checking on PRep Distribution:
```{r}
p1.prep.agyw %>% 
  ggplot() + 
    geom_point(mapping = aes(x = Year, y = PrEP_F1524_M, color = scenario_name))

p2.prep.fsw %>% 
  ggplot() + 
    geom_point(mapping = aes(x = Year, y = PrEP_FSW1599_M, color = scenario_name))
  
p3.prep.sd %>% 
  ggplot() + 
    geom_point(mapping = aes(x = Year, y = PrEP_SDCA1599_M, color = scenario_name))

p4.prep.plw %>% 
  ggplot() + 
    geom_point(mapping = aes(x = Year, y = PrEP_pregbfF1549_M, color = scenario_name))
```


## Output Flow Variables
For each of the separate scenarios, need to 
1. select the right set of columns
2. make sure those columns are named appropriately (tdf/cab/etc)

### Set up flow variables
```{r}
flow.variables.sheet <- merge(
  inc.summary, NHIVInf.summary, by = c('Year', 'scenario_name')) %>% 
  merge(HIVDeaths.summary, by = c('Year', 'scenario_name')) %>% 
  merge(TOTDeaths.summary, by = c('Year', 'scenario_name')) %>% 
  merge(yll.summary, by = c('Year', 'scenario_name')) %>% 
  merge(Testing.summary, by = c('Year', 'scenario_name')) %>% 
  merge(VMMC.summary, by = c('Year', 'scenario_name'))
```

### Functions for writing out different scenarios

Different scenarios will have different columns in them, because not every scenario receives every kind of intervention.

Make sure that the name of the output file is set correctly, otherwise you might overwrite your work

#### Minimal and VMMC scenario output
```{r}
output.file.name = "" # MIHPSA_ZWE_Phase2_minimal_[group name]_flow.csv

write_csv(
  flow.variables.sheet %>% 
    filter(Year >= 2022), 
  file = output.file.name
  )

```

### Save TDF Variable template sheets, also status quo

These include extra columns for TDF distribution.

This can also be used for Status Quo scenario, since that includes TDF
```{r}
output.file.name = "" # MIHPSA_ZWE_Phase2_TDF_[group name]_flow.csv

tdf.output.table <- merge(
  flow.variables.sheet %>% 
    filter(Year >= 2022),
  p1.prep.agyw %>% 
    filter(Year >= 2022),
  by = c('Year', 'scenario_name')
) %>% 
  mutate(NTDFPrEP_F1524_M = PrEP_F1524_M) %>% 
  select(-PrEP_F1524_M) 

tdf.output.table %>% 
  write_csv(file = output.file.name)
```


### Save DPVR Variable template sheets 

These include extra columns for DPVR distribution
```{r}
output.file.name = "" # MIHPSA_ZWE_Phase2_DPVR_[group name]_flow.csv

dpvr.output.table <- merge(
  flow.variables.sheet %>% 
    filter(Year >= 2022),
  p1.prep.agyw %>% 
    filter(Year >= 2022),
  by = c('Year', 'scenario_name')
) %>% 
  mutate(NDPVPrEP_F1524_M = PrEP_F1524_M) %>% 
  select(-PrEP_F1524_M) 


dpvr.output.table %>% 
  write_csv(file = output.file.name)
```

### Save CAB-LA Variable template sheets

These include extra columns for CAB-LA distribution

```{r}

output.file.name = "" # MIHPSA_ZWE_Phase2_CABLA_[group name]_flow.csv

cabla.output.table <-  merge(
  flow.variables.sheet %>% 
    filter(Year >= 2022),
  p1.prep.agyw %>% 
    filter(Year >= 2022),
  by = c('Year', 'scenario_name')
) %>% 
  mutate(NCABPrEP_F1524_M = PrEP_F1524_M) %>% 
  select(-PrEP_F1524_M) 

cabla.output.table %>% 
  write_csv(file = output.file.name)


```


# Stock Variables

*Every half-year for stock variables

## HIV Prevalence

```{r}
# HIVprev_M1549_M
p1 <- sim.results.all %>% 
  filter(Age >=15, Age<50, Gender == 0) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(pop > 0 ~ PLHIV/pop,
                          pop == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(HIVprev_M1549_M_sd = sd(prev), 
            HIVprev_M1549_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVprev_M1549_95LL = lower_ci(HIVprev_M1549_M, HIVprev_M1549_M_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVprev_M1549_95UL = upper_ci(HIVprev_M1549_M, HIVprev_M1549_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-HIVprev_M1549_M_sd)

# HIVprev_F1549_M
p2 <- sim.results.all %>% 
  filter(Age >=15, Age<50, Gender == 1) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(pop > 0 ~ PLHIV/pop,
                          pop == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(HIVprev_F1549_M_sd = sd(prev), 
            HIVprev_F1549_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVprev_F1549_95LL = lower_ci(HIVprev_F1549_M, HIVprev_F1549_M_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVprev_F1549_95UL = upper_ci(HIVprev_F1549_M, HIVprev_F1549_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-HIVprev_F1549_M_sd)

# HIVprev_A1549_M
p3 <- sim.results.all %>% 
  filter(Age >=15, Age<50) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(pop > 0 ~ PLHIV/pop,
                          pop == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(HIVprev_A1549_M_sd = sd(prev), 
            HIVprev_A1549_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVprev_A1549_95LL = lower_ci(HIVprev_A1549_M, HIVprev_A1549_M_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVprev_A1549_95UL = upper_ci(HIVprev_A1549_M, HIVprev_A1549_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-HIVprev_A1549_M_sd)

# HIVprev_F1524_M
p4 <- sim.results.all %>% 
  filter(Age >=15, Age<25, Gender == 1) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(pop > 0 ~ PLHIV/pop,
                          pop == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(HIVprev_F1524_M_sd = sd(prev), 
            HIVprev_F1524_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVprev_F1524_95LL = lower_ci(HIVprev_F1524_M, HIVprev_F1524_M_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVprev_F1524_95UL = upper_ci(HIVprev_F1524_M, HIVprev_F1524_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-HIVprev_F1524_M_sd)

# HIVprev_FSW1599_M
p5 <- sim.results.all %>% 
  filter(Age >=15, Gender == 1, IP_Key.Risk == "HIGH") %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(pop > 0 ~ PLHIV/pop,
                          pop == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(HIVprev_FSW1599_M_sd = sd(prev), 
            HIVprev_FSW1599_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVprev_FSW1599_95LL = lower_ci(HIVprev_FSW1599_M, HIVprev_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVprev_FSW1599_95UL = upper_ci(HIVprev_FSW1599_M, HIVprev_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-HIVprev_FSW1599_M_sd)

HIVprev.summary <- merge(p1, p2, by = c('Year', 'scenario_name')) %>% 
  merge(p3, by = c('Year', 'scenario_name')) %>% 
  merge(p4, by = c('Year', 'scenario_name')) %>% 
  merge(p5, by = c('Year', 'scenario_name')) %>% 
  mutate(Year = floor(Year)) 
```

## Population

```{r}
# NAlive_M1599_M
p1 <- sim.results.all %>% 
  #filter(Age >=15, Gender == 0) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NAlive_M1599_M = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NAlive_M1599_M_sd = sd(NAlive_M1599_M), 
            NAlive_M1599_M = mean(NAlive_M1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_M1599_95LL = lower_ci(NAlive_M1599_M, NAlive_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_M1599_95UL = upper_ci(NAlive_M1599_M, NAlive_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_M1599_M_sd)

# NAlive_F1599_M
p2 <- sim.results.all %>% 
  filter(Age >=15, Gender == 1) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NAlive_F1599_M = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NAlive_F1599_M_sd = sd(NAlive_F1599_M), 
            NAlive_F1599_M = mean(NAlive_F1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_F1599_95LL = lower_ci(NAlive_F1599_M, NAlive_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_F1599_95UL = upper_ci(NAlive_F1599_M, NAlive_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_F1599_M_sd)

# NAlive_A014_M
p3 <- sim.results.all %>% 
  filter(Age <15) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NAlive_A014_M = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NAlive_A014_M_sd = sd(NAlive_A014_M), 
            NAlive_A014_M = mean(NAlive_A014_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_A014_95LL = lower_ci(NAlive_A014_M, NAlive_A014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_A014_95UL = upper_ci(NAlive_A014_M, NAlive_A014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_A014_M_sd)


# NAlive_M1524_M
p4 <- sim.results.all %>% 
  filter(Age >=15, Age <25, Gender == 0) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NAlive_M1524_M = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NAlive_M1524_M = mean(NAlive_M1524_M), 
            .groups = 'keep') %>% 
  ungroup()

# NAlive_F1524_M
p5 <- sim.results.all %>% 
  filter(Age >=15, Age <25, Gender == 1) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NAlive_F1524_M = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NAlive_F1524_M = mean(NAlive_F1524_M), 
            .groups = 'keep') %>% 
  ungroup()

# NAlive_M2549_M
p6 <- sim.results.all %>% 
  filter(Age >=25, Age <50, Gender == 0) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NAlive_M2549_M = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NAlive_M2549_M = mean(NAlive_M2549_M), 
            .groups = 'keep') %>% 
  ungroup()

# NAlive_F2549_M
p7 <- sim.results.all %>% 
  filter(Age >=25, Age <50, Gender == 1) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NAlive_F2549_M = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NAlive_F2549_M = mean(NAlive_F2549_M), 
            .groups = 'keep') %>% 
  ungroup()

# NAlive_FSW1599_M
p8 <- sim.results.all %>% 
  filter(#Age >=15, 
         
         Gender == 1, IP_Key.Risk == "HIGH") %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NAlive_FSW1599_M = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NAlive_FSW1599_M_sd = sd(NAlive_FSW1599_M), 
            NAlive_FSW1599_M = mean(NAlive_FSW1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_FSW1599_95LL = lower_ci(NAlive_FSW1599_M, NAlive_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_FSW1599_95UL = upper_ci(NAlive_FSW1599_M, NAlive_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_FSW1599_M_sd)

NAlive.summary <- merge(p1, p2, by = c('Year', 'scenario_name')) %>% 
  merge(p3, by = c('Year', 'scenario_name')) %>% 
  merge(p4, by = c('Year', 'scenario_name')) %>% 
  merge(p5, by = c('Year', 'scenario_name')) %>% 
  merge(p6, by = c('Year', 'scenario_name')) %>% 
  merge(p7, by = c('Year', 'scenario_name')) %>% 
  merge(p8, by = c('Year', 'scenario_name')) %>% 
  mutate(Year = floor(Year)) 
```

## PLHIV 
```{r}
# NHIV_M1599_M
p1 <- sim.results.all %>% 
  #filter(Age >=15, Gender == 0) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NHIV_M1599_M = sum(Infected * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_M1599_M_sd = sd(NHIV_M1599_M), 
            NHIV_M1599_M = mean(NHIV_M1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIV_M1599_95LL = lower_ci(NHIV_M1599_M, NHIV_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIV_M1599_95UL = upper_ci(NHIV_M1599_M, NHIV_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIV_M1599_M_sd)

# NHIV_F1599_M
p2 <- sim.results.all %>% 
#  filter(Age >=15, Gender == 1) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NHIV_F1599_M = sum(Infected * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_F1599_M_sd = sd(NHIV_F1599_M), 
            NHIV_F1599_M = mean(NHIV_F1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIV_F1599_95LL = lower_ci(NHIV_F1599_M, NHIV_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIV_F1599_95UL = upper_ci(NHIV_F1599_M, NHIV_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIV_F1599_M_sd)

# NHIV_A014_M
p3 <- sim.results.all %>% 
  filter(Age <15) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NHIV_A014_M = sum(Infected * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_A014_M_sd = sd(NHIV_A014_M), 
            NHIV_A014_M = mean(NHIV_A014_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIV_A014_95LL = lower_ci(NHIV_A014_M, NHIV_A014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIV_A014_95UL = upper_ci(NHIV_A014_M, NHIV_A014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIV_A014_M_sd)


# NHIV_M1524_M
p4 <- sim.results.all %>% 
  filter(Age >=15, Age <25, Gender == 0) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NHIV_M1524_M = sum(Infected * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_M1524_M = mean(NHIV_M1524_M), 
            .groups = 'keep') %>% 
  ungroup()

# NHIV_F1524_M
p5 <- sim.results.all %>% 
  filter(Age >=15, Age <25, Gender == 1) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NHIV_F1524_M = sum(Infected * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_F1524_M = mean(NHIV_F1524_M), 
            .groups = 'keep') %>% 
  ungroup()

# NHIV_M2549_M
p6 <- sim.results.all %>% 
  filter(Age >=25, Age <50, Gender == 0) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NHIV_M2549_M = sum(Infected * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_M2549_M = mean(NHIV_M2549_M), 
            .groups = 'keep') %>% 
  ungroup()

# NHIV_F2549_M
p7 <- sim.results.all %>% 
  filter(Age >=25, Age <50, Gender == 1) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NHIV_F2549_M = sum(Infected * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_F2549_M = mean(NHIV_F2549_M), 
            .groups = 'keep') %>% 
  ungroup()

# NHIV_FSW1599_M
p8 <- sim.results.all %>% 
  filter(#Age >=15, 
    Gender == 1, IP_Key.Risk == "HIGH") %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(NHIV_FSW1599_M = sum(Infected * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_FSW1599_M_sd = sd(NHIV_FSW1599_M), 
            NHIV_FSW1599_M = mean(NHIV_FSW1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIV_FSW1599_95LL = lower_ci(NHIV_FSW1599_M, NHIV_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIV_FSW1599_95UL = upper_ci(NHIV_FSW1599_M, NHIV_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIV_FSW1599_M_sd)

NHIV.summary <- merge(p1, p2, by = c('Year', 'scenario_name')) %>% 
  merge(p3, by = c('Year', 'scenario_name')) %>% 
  merge(p4, by = c('Year', 'scenario_name')) %>% 
  merge(p5, by = c('Year', 'scenario_name')) %>% 
  merge(p6, by = c('Year', 'scenario_name')) %>% 
  merge(p7, by = c('Year', 'scenario_name')) %>% 
  merge(p8, by = c('Year', 'scenario_name')) %>% 
  mutate(Year = floor(Year)) 
```

## CD4 Counts

```{r}
# Number of 15+ PLHIV not on treatment, with CD4 >= 500
# NHIV_A1599_NoART_CD4500pl_M
p1 <- sim.results.all %>% 
  filter(Age >= 15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(Infected.CD4.500.Plus..Not.On.ART. = sum(Infected.CD4.500.Plus..Not.On.ART. * pop.scaling.factor), 
            .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_A1599_NoART_CD4500pl_M = mean(Infected.CD4.500.Plus..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 350 <= CD4 < 500
#NHIV_A1599_NoART_CD4350499_M
p2 <- sim.results.all %>% 
  filter(Age >= 15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(Infected.CD4.350.To.499..Not.On.ART. = sum(Infected.CD4.350.To.499..Not.On.ART.* pop.scaling.factor ), 
            .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_A1599_NoART_CD4350499_M = mean(Infected.CD4.350.To.499..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 200 <= CD4 < 350
# NHIV_A1599_NoART_CD4200349_M
p3  <- sim.results.all %>% 
  filter(Age >= 15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(Infected.CD4.200.To.349..Not.On.ART. = sum(Infected.CD4.200.To.349..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_A1599_NoART_CD4200349_M = mean(Infected.CD4.200.To.349..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 50 <= CD4 < 200
# NHIV_A1599_NoART_CD450199_M
p4a  <- sim.results.all %>% 
  filter(Age >= 15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor)*7/8, .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_A1599_NoART_CD450199_M = mean(Infected.CD4.Under.200..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 0 <= CD4 < 50
# NHIV_A1599_NoART_CD4050_M
p4b  <- sim.results.all %>% 
  filter(Age >= 15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor)/8, .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_A1599_NoART_CD4050_M = mean(Infected.CD4.Under.200..Not.On.ART.))


# Number of 0-14yo PLHIV not on treatment, with CD4 >= 500
# NHIV_A014_NoART_CD4500pl_M
p5 <- sim.results.all %>% 
  filter(Age < 15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(Infected.CD4.500.Plus..Not.On.ART. = sum(Infected.CD4.500.Plus..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_A014_NoART_CD4500pl_M = mean(Infected.CD4.500.Plus..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 350 <= CD4 < 500
# NHIV_A014_NoART_CD4350499_M
p6 <- sim.results.all %>% 
  filter(Age < 15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(Infected.CD4.200.To.349..Not.On.ART. = sum(Infected.CD4.200.To.349..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_A014_NoART_CD4350499_M = mean(Infected.CD4.200.To.349..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 200 <= CD4 < 350
# NHIV_A014_NoART_CD4200349_M
p7 <- sim.results.all %>% 
  filter(Age < 15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(Infected.CD4.350.To.499..Not.On.ART. = sum(Infected.CD4.350.To.499..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_A014_NoART_CD4200349_M = mean(Infected.CD4.350.To.499..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 0 <= CD4 < 200
# NHIV_A014_NoART_CD450199_M
p8a <- sim.results.all %>% 
  filter(Age < 15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor)*7/8, .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_A014_NoART_CD450199_M = mean(Infected.CD4.Under.200..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 0 <= CD4 < 200
# NHIV_A014_NoART_CD4050_M
p8b <- sim.results.all %>% 
  filter(Age < 15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor)/8, .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NHIV_A014_NoART_CD4050_M = mean(Infected.CD4.Under.200..Not.On.ART.))

ylds.current.summary <- merge(p1, p2, by = c('Year', 'scenario_name')) %>% 
  merge(p3, by = c('Year', 'scenario_name')) %>% 
  merge(p4a, by = c('Year', 'scenario_name')) %>% 
  merge(p4b, by = c('Year', 'scenario_name')) %>% 
  merge(p5, by = c('Year', 'scenario_name')) %>% 
  merge(p6, by = c('Year', 'scenario_name')) %>% 
  merge(p7, by = c('Year', 'scenario_name')) %>% 
  merge(p8a, by = c('Year', 'scenario_name')) %>% 
  merge(p8b, by = c('Year', 'scenario_name')) %>% 
  mutate(Year = floor(Year)) 
```

## Diagnosed
```{r}
# P_DIAG_A1599_M
p1 <- sim.results.all %>% 
  filter(Age >=15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(diag = sum(Diagnosed * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(PLHIV > 0 ~ diag/PLHIV,
                          PLHIV == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_DIAG_A1599_M_sd = sd(prev), 
            P_DIAG_A1599_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_DIAG_A1599_95LL = lower_ci(P_DIAG_A1599_M, P_DIAG_A1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_DIAG_A1599_95UL = upper_ci(P_DIAG_A1599_M, P_DIAG_A1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_DIAG_A1599_M_sd)

# P_DIAG_M1599_M
p2 <- sim.results.all %>% 
  filter(Age >=15, Gender == 0) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(diag = sum(Diagnosed * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(PLHIV > 0 ~ diag/PLHIV,
                          PLHIV == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_DIAG_M1599_M_sd = sd(prev), 
            P_DIAG_M1599_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_DIAG_M1599_95LL = lower_ci(P_DIAG_M1599_M, P_DIAG_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_DIAG_M1599_95UL = upper_ci(P_DIAG_M1599_M, P_DIAG_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_DIAG_M1599_M_sd)

# P_DIAG_F1599_M
p3 <- sim.results.all %>% 
  filter(Age >=15, Gender == 1) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(diag = sum(Diagnosed * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(PLHIV > 0 ~ diag/PLHIV,
                          PLHIV == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_DIAG_F1599_M_sd = sd(prev), 
            P_DIAG_F1599_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_DIAG_F1599_95LL = lower_ci(P_DIAG_F1599_M, P_DIAG_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_DIAG_F1599_95UL = upper_ci(P_DIAG_F1599_M, P_DIAG_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_DIAG_F1599_M_sd)

# P_DIAG_A014_M
p4 <- sim.results.all %>% 
  filter(Age<15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(diag = sum(Diagnosed * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(PLHIV > 0 ~ diag/PLHIV,
                          PLHIV == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_DIAG_A014_M_sd = sd(prev), 
            P_DIAG_A014_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_DIAG_A014_95LL = lower_ci(P_DIAG_A014_M, P_DIAG_A014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_DIAG_A014_95UL = upper_ci(P_DIAG_A014_M, P_DIAG_A014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_DIAG_A014_M_sd)

# P_DIAG_M1524_M
p5 <- sim.results.all %>% 
  filter(Age >=15, Age < 25, Gender == 0) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(diag = sum(Diagnosed * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(PLHIV > 0 ~ diag/PLHIV,
                          PLHIV == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_DIAG_M1524_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup()

# P_DIAG_F1524_M
p6 <- sim.results.all %>% 
  filter(Age >=15, Gender == 1) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(diag = sum(Diagnosed * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(PLHIV > 0 ~ diag/PLHIV,
                          PLHIV == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_DIAG_F1524_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() 

# P_DIAG_FSW1599_M
p7 <- sim.results.all %>% 
  filter(Age >=15, Gender == 1, IP_Key.Risk == "HIGH") %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(diag = sum(Diagnosed * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(PLHIV > 0 ~ diag/PLHIV,
                          PLHIV == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_DIAG_FSW1599_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() 

Diagnosed.summary <- merge(p1, p2, by = c('Year', 'scenario_name')) %>% 
  merge(p3, by = c('Year', 'scenario_name')) %>% 
  merge(p4, by = c('Year', 'scenario_name')) %>% 
  merge(p5, by = c('Year', 'scenario_name')) %>% 
  merge(p6, by = c('Year', 'scenario_name')) %>% 
  merge(p7, by = c('Year', 'scenario_name')) %>% 
  mutate(Year = floor(Year)) 
```

## ART

```{r}
# NOnART_M1599_M
# number of males on art, age 15-99
p1 <- sim.results.all %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(NOnART_M1599_M = sum(On_ART * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NOnART_M1599_M_sd = sd(NOnART_M1599_M), 
            NOnART_M1599_M = mean(NOnART_M1599_M), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NOnART_M1599_95LL = lower_ci(NOnART_M1599_M, NOnART_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NOnART_M1599_95UL = upper_ci(NOnART_M1599_M, NOnART_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% select(-NOnART_M1599_M_sd)

# Number Female adults on ART
# NOnART_F1599_M
p2 <- sim.results.all %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(NOnART_F1599_M = sum(On_ART  * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NOnART_F1599_M_sd = sd(NOnART_F1599_M), 
            NOnART_F1599_M = mean(NOnART_F1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NOnART_F1599_95LL = lower_ci(NOnART_F1599_M, NOnART_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NOnART_F1599_95UL = upper_ci(NOnART_F1599_M, NOnART_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% select(-NOnART_F1599_M_sd)

# Number adolescents on ART 
# NOnART_A1524_M
p3 <- sim.results.all %>% 
  filter(Age >=15, Age <25) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(NOnART_A1524_M = sum(On_ART  * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NOnART_A1524_M_sd = sd(NOnART_A1524_M), 
            NOnART_A1524_M = mean(NOnART_A1524_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NOnART_A1524_95LL = lower_ci(NOnART_A1524_M, NOnART_A1524_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NOnART_A1524_95UL = upper_ci(NOnART_A1524_M, NOnART_A1524_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% select(-NOnART_A1524_M_sd)

# Number adults on ART
# NOnART_A099_M
p4 <- sim.results.all %>% 
  filter(Age >=15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(NOnART_A099_M = sum(On_ART  * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NOnART_A099_M_sd = sd(NOnART_A099_M), 
            NOnART_A099_M = mean(NOnART_A099_M), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NOnART_A099_95LL = lower_ci(NOnART_A099_M, NOnART_A099_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NOnART_A099_95UL = upper_ci(NOnART_A099_M, NOnART_A099_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% select(-NOnART_A099_M_sd)

# Number children on ART
# NOnART_A014_M
p5 <- sim.results.all %>% 
  filter(Age < 15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(NOnART_A014_M = sum(On_ART  * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year, scenario_name) %>% 
  summarize(NOnART_A014_M_sd = sd(NOnART_A014_M), 
            NOnART_A014_M = mean(NOnART_A014_M), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NOnART_A014_95LL = lower_ci(NOnART_A014_M, NOnART_A014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NOnART_A014_95UL = upper_ci(NOnART_A014_M, NOnART_A014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% select(-NOnART_A014_M_sd)

NOnART.summary <- merge(p1, p2, by = c('Year', 'scenario_name')) %>% 
  merge(p3, by = c('Year', 'scenario_name')) %>% 
  merge(p4, by = c('Year', 'scenario_name')) %>% 
  merge(p5, by = c('Year', 'scenario_name')) %>% 
  mutate(Year = floor(Year)) 

```

## Percent diagnosed on ART

```{r}
# P_onART_DiagM1599_M
p1 <- sim.results.all %>% 
  filter(Age >=15, Gender == 0) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(onart = sum(On_ART * pop.scaling.factor), 
            diag = sum(Diagnosed*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(diag > 0 ~ onart/diag,
                          diag == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_onART_DiagM1599_M_sd = sd(prev), 
            P_onART_DiagM1599_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_DiagM1599_95LL = lower_ci(P_onART_DiagM1599_M, P_onART_DiagM1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_DiagM1599_95UL = upper_ci(P_onART_DiagM1599_M, P_onART_DiagM1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_onART_DiagM1599_M_sd)

# P_onART_DiagF1599_M
p2 <- sim.results.all %>% 
  filter(Age >=15, Gender == 1) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(onart = sum(On_ART * pop.scaling.factor), 
            diag = sum(Diagnosed*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(diag > 0 ~ onart/diag,
                          diag == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_onART_DiagF1599_M_sd = sd(prev), 
            P_onART_DiagF1599_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_DiagF1599_95LL = lower_ci(P_onART_DiagF1599_M, P_onART_DiagF1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_DiagF1599_95UL = upper_ci(P_onART_DiagF1599_M, P_onART_DiagF1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_onART_DiagF1599_M_sd)

# P_onART_DiagM1524_M
p3 <- sim.results.all %>% 
  filter(Age >=15, Age < 25, Gender == 0) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(onart = sum(On_ART * pop.scaling.factor), 
            diag = sum(Diagnosed*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(diag > 0 ~ onart/diag,
                          diag == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_onART_DiagM1524_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup()

# P_onART_DiagF1524_M
p4 <- sim.results.all %>% 
  filter(Age >=15, Age < 25, Gender == 1) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(onart = sum(On_ART * pop.scaling.factor), 
            diag = sum(Diagnosed*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(diag > 0 ~ onart/diag,
                          diag == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_onART_DiagF1524_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() 

# P_onART_DiagA1599_M
p5 <- sim.results.all %>% 
  filter(Age >=15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(onart = sum(On_ART * pop.scaling.factor), 
            diag = sum(Diagnosed*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(diag > 0 ~ onart/diag,
                          diag == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_onART_DiagA1599_M_sd = sd(prev), 
            P_onART_DiagA1599_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_DiagA1599_95LL = lower_ci(P_onART_DiagA1599_M, P_onART_DiagA1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_DiagA1599_95UL = upper_ci(P_onART_DiagA1599_M, P_onART_DiagA1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_onART_DiagA1599_M_sd)

# P_onART_DiagA014_M
p6 <- sim.results.all %>% 
  filter(Age<15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(onart = sum(On_ART * pop.scaling.factor), 
            diag = sum(Diagnosed*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(diag > 0 ~ onart/diag,
                          diag == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_onART_DiagA014_M_sd = sd(prev), 
            P_onART_DiagA014_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_DiagA014_95LL = lower_ci(P_onART_DiagA014_M, P_onART_DiagA014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_DiagA014_95UL = upper_ci(P_onART_DiagA014_M, P_onART_DiagA014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_onART_DiagA014_M_sd)


# P_onART_DiagFSW1599_M
p7 <- sim.results.all %>% 
  filter(Age >=15, Gender == 1, IP_Key.Risk == "HIGH") %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(onart = sum(On_ART * pop.scaling.factor), 
            diag = sum(Diagnosed*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(diag > 0 ~ onart/diag,
                          diag == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_onART_DiagFSW1599_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() 

PonART.summary <- merge(p1, p2, by = c('Year', 'scenario_name')) %>% 
  merge(p3, by = c('Year', 'scenario_name')) %>% 
  merge(p4, by = c('Year', 'scenario_name')) %>% 
  merge(p5, by = c('Year', 'scenario_name')) %>% 
  merge(p6, by = c('Year', 'scenario_name')) %>% 
  merge(p7, by = c('Year', 'scenario_name')) %>% 
  mutate(Year = floor(Year)) 
```

## P_onart_HIV
```{r}
# P_onART_HIVM1599_M
p1 <- sim.results.all %>% 
  filter(Age >=15, Gender == 0) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(onart = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(PLHIV > 0 ~ onart/PLHIV,
                          PLHIV == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_onART_HIVM1599_M_sd = sd(prev), 
            P_onART_HIVM1599_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_HIVM1599_95LL = lower_ci(P_onART_HIVM1599_M, P_onART_HIVM1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_HIVM1599_95UL = upper_ci(P_onART_HIVM1599_M, P_onART_HIVM1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_onART_HIVM1599_M_sd)

# P_onART_HIVF1599_M
p2 <- sim.results.all %>% 
  filter(Age >=15, Gender == 1) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(onart = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(PLHIV > 0 ~ onart/PLHIV,
                          PLHIV == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_onART_HIVF1599_M_sd = sd(prev), 
            P_onART_HIVF1599_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_HIVF1599_95LL = lower_ci(P_onART_HIVF1599_M, P_onART_HIVF1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_HIVF1599_95UL = upper_ci(P_onART_HIVF1599_M, P_onART_HIVF1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_onART_HIVF1599_M_sd)

# P_onART_HIVM1524_M
p3 <- sim.results.all %>% 
  filter(Age >=15, Age < 25, Gender == 0) %>%
  group_by(Year, scenario_name, sim.ix) %>% 
  summarize(onart = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(PLHIV > 0 ~ onart/PLHIV,
                          PLHIV == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_onART_HIVM1524_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup()

# P_onART_HIVF1524_M
p4 <- sim.results.all %>% 
  filter(Age >=15, Age < 25, Gender == 1) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(onart = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(PLHIV > 0 ~ onart/PLHIV,
                          PLHIV == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_onART_HIVF1524_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() 

# P_onART_HIVA1599_M
p5 <- sim.results.all %>% 
  filter(Age >=15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(onart = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(PLHIV > 0 ~ onart/PLHIV,
                          PLHIV == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_onART_HIVA1599_M_sd = sd(prev), 
            P_onART_HIVA1599_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_HIVA1599_95LL = lower_ci(P_onART_HIVA1599_M, P_onART_HIVA1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_HIVA1599_95UL = upper_ci(P_onART_HIVA1599_M, P_onART_HIVA1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_onART_HIVA1599_M_sd)

# P_onART_HIVA014_M
p6 <- sim.results.all %>% 
  filter(Age<15) %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(onart = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(PLHIV > 0 ~ onart/PLHIV,
                          PLHIV == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_onART_HIVA014_M_sd = sd(prev), 
            P_onART_HIVA014_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_HIVA014_95LL = lower_ci(P_onART_HIVA014_M, P_onART_HIVA014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_HIVA014_95UL = upper_ci(P_onART_HIVA014_M, P_onART_HIVA014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_onART_HIVA014_M_sd)


# P_onART_HIVFSW1599_M
p7 <- sim.results.all %>% 
  filter(Age >=15, Gender == 1, IP_Key.Risk == "HIGH") %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(onart = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(PLHIV > 0 ~ onart/PLHIV,
                          PLHIV == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(P_onART_HIVFSW1599_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() 

PonART_HIV.summary <- merge(p1, p2, by = c('Year', 'scenario_name')) %>% 
  merge(p3, by = c('Year', 'scenario_name')) %>% 
  merge(p4, by = c('Year', 'scenario_name')) %>% 
  merge(p5, by = c('Year', 'scenario_name')) %>% 
  merge(p6, by = c('Year', 'scenario_name')) %>% 
  merge(p7, by = c('Year', 'scenario_name')) %>% 
  mutate(Year = floor(Year)) 
```

## Fraction on PrEP
Number young women at elevated risk alive at elevated risk
Fraction of adolescent young females at elevated risk on PrEP

```{r}
PonPrEP.summary <- sim.results.all %>% 
  filter(Age >=15, Age < 25, Gender == 1, IP_Key.Risk == "HIGH") %>% 
  group_by(Year, scenario_name, sim.id) %>% 
  summarize(Population = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor),
            ReceivePrEP_HIGH = sum(ReceivePrEP_HIGH * pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>%
  mutate(PLWHIV = Population - PLHIV) %>% 
  mutate(prev = case_when(PLWHIV > 0 ~ 100*ReceivePrEP_HIGH/PLWHIV,
                          PLWHIV == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(
    NAlive_ElevRiskF1524_M = mean(PLWHIV), 
    P_PrEP_ElevRiskF1524_M = mean(prev), 
    .groups = 'keep') %>% 
  ungroup() 
```


## Fraction circumcised

```{r}
VMMC.fraction.summary <- merge(
  sim.results.all %>% 
    filter(Age >= 15, Age<50, Gender == 0) %>% 
    group_by(Year, scenario_name, sim.id) %>%
    summarize(Population = sum(Population * pop.scaling.factor)) %>% ungroup(),
  sim.results.all %>% 
    filter(Age >= 15, Age<50, Gender == 0, IsCircumcised == 1) %>% 
    group_by(Year, scenario_name, sim.id) %>%
    summarize(CircPop = sum(Population * pop.scaling.factor)) %>% ungroup(),
  by = c("Year", "scenario_name", "sim.id")
) %>% 
  mutate(CIRC_PREV_M1549_M = case_when(Population > 0 ~ 100*CircPop/Population,
                                       Population == 0 ~ 0)) %>% 
  group_by(Year, scenario_name) %>% 
  summarize(CIRC_PREV_M1549_M_sd = sd(CIRC_PREV_M1549_M), 
            CIRC_PREV_M1549_M = mean(CIRC_PREV_M1549_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    CIRC_PREV_M1549_M_95LL = lower_ci(CIRC_PREV_M1549_M, CIRC_PREV_M1549_M_sd/sqrt(nruns), nruns, conf_level = .95),
    CIRC_PREV_M1549_M_95UL = upper_ci(CIRC_PREV_M1549_M, CIRC_PREV_M1549_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-CIRC_PREV_M1549_M_sd)

```



## Write out Stock Variables
```{r}
stock.variables.sheet <- merge(
  HIVprev.summary, HIVprev.summary, by = c('Year', 'scenario_name')) %>% 
  merge(NAlive.summary, by = c('Year', 'scenario_name')) %>% 
  merge(NHIV.summary, by = c('Year', 'scenario_name')) %>% 
  merge(ylds.current.summary, by = c('Year', 'scenario_name')) %>% 
  merge(Diagnosed.summary, by = c('Year', 'scenario_name')) %>% 
  merge(NOnART.summary, by = c('Year', 'scenario_name')) %>% 
  merge(PonART.summary, by = c('Year', 'scenario_name')) %>% 
  merge(PonART_HIV.summary, by = c('Year', 'scenario_name')) %>% 
  merge(VMMC.fraction.summary, by = c('Year', 'scenario_name'))
```

### Minimal and VMMC
```{r}
output.file.name = "MIHPSA_ZWE_Phase2_minimal_stock.csv"

write_csv(
  stock.variables.sheet %>% 
    filter(Year >= 2023), 
  file = output.file.name
  )
```


### TDF Variable template 

```{r}
output.file.name = "MIHPSA_ZWE_Phase2_TDF_[target]_stock.csv"

agyw.output <- stock.variables.sheet %>% 
  filter(Year >= 2022, scenario_name == "tdf.agyw") %>% 
  merge(PonPrEP.summary,  by = c('Year', 'scenario_name')) %>% 
  mutate(P_TDFPrEP_ElevRiskF1524_M = P_PrEP_ElevRiskF1524_M) %>%
  select(-P_PrEP_ElevRiskF1524_M) 

agyw.output %>% 
  write_csv(output.file.name)

```

### Save DPVR templates

```{r}
output.file.name = "MIHPSA_ZWE_Phase2_DPV_[target]_stock.csv"

agyw.output <- stock.variables.sheet %>% 
  filter(Year >= 2022, scenario_name == "dpvr.agyw") %>% 
  merge(PonPrEP.summary,  by = c('Year', 'scenario_name')) %>% 
  mutate(P_DPVPrEP_ElevRiskF1524_M = P_PrEP_ElevRiskF1524_M) %>%
  select(-P_PrEP_ElevRiskF1524_M) 

agyw.output %>% 
  write_csv(output.file.name)

```


### CABLA Variable Template

```{r}
output.file.name = "MIHPSA_ZWE_Phase2_CABLA_[target]_stock.csv"

stock.variables.sheet %>% 
  filter(Year >= 2022, scenario_name == "cabla.agyw") %>% 
  merge(PonPrEP.summary,  by = c('Year', 'scenario_name')) %>% 
  mutate(P_CABPrEP_ElevRiskF1524_M = P_PrEP_ElevRiskF1524_M) %>%
  select(-P_PrEP_ElevRiskF1524_M) %>% 
  write_csv(output.file.name)

```

