---
title: "ZWE_MIHPSA_Phase_2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Load libraries}
library(tidyverse)
library(tidyr)
library(data.table)
library(magrittr)
library(ggplot2)
library(devtools)
devtools::install_github("BershteynLab/EMODAnalyzeR")

```

```{r Functions}

# Confidence interval functions
lower_ci <- function(mean, se, n, conf_level = 0.95){
  lower_ci <- mean - qt(1 - ((1 - conf_level) / 2), n - 1) * se/sqrt(n)
}
upper_ci <- function(mean, se, n, conf_level = 0.95){
  upper_ci <- mean + qt(1 - ((1 - conf_level) / 2), n - 1) * se/sqrt(n)
}
```


# Postprocessing Zimbabwe Model

The purpose of this notebook is to perform postprocessing and analysis of the initial Phase 2 scenarios for the Zimbabwe MIHPSA collaboration.

There are two sets of outputs to analyze:

* "Essential Scenario" - baseline, with no PrEP
* Essential Scenario + PrEP - adding 45k PrEP initiations per year after 2020 or so.


# Read in Simulation Data

## Read in Essential Scenario Simulation

```{r}
#res_path = "/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/ZWE_phase2/Baseline-campaign_ZWE_MIHPSA_2023_noprep-noprep/ReportHIVByAgeAndGender"
res.path.prep = "/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/ZWE_phase2_2/Baseline-campaign_ZWE_MIHPSA_2023_noprep-noprep/ReportHIVByAgeAndGender"

sim.results.base <- EMODAnalyzeR::read.simulation.results(
  results_path  = res.path.prep,
  scenario_name = 'prep',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed", 
                        "Newly.Tested.Positive", "Newly.Tested.Negative","HIVPositiveHIVTest","HIVNegativeHIVTest",
                        "Needs_PMTCT_Diagnostic_Test","NewlySymptomatic",
                        "Infected.CD4.Under.200..Not.On.ART.", "Infected.CD4.200.To.349..Not.On.ART.",
                        "Infected.CD4.350.To.499..Not.On.ART.", "Infected.CD4.500.Plus..Not.On.ART."),
                        #"ReceivePrEP_HIGH"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.Risk"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)

```

## Read in PrEP Scenario Simulation Runs
```{r Read in PrEP Scenario Simulation Runs}

res_path = "/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/ZWE_phase2/Baseline-campaign_ZWE_MIHPSA_2023-prep/ReportHIVByAgeAndGender"

sim.results.prep <- EMODAnalyzeR::read.simulation.results(
  results_path  = res_path,
  scenario_name = 'prep',
  summarize_columns = c("Population","Infected", "On_ART",
                        "Died", "Died_from_HIV",
                        "Newly.Infected","Diagnosed", 
                        "Infected.CD4.Under.200..Not.On.ART.", "Infected.CD4.200.To.349..Not.On.ART.",
                        "Infected.CD4.350.To.499..Not.On.ART.", "Infected.CD4.500.Plus..Not.On.ART.",
                        "ReceivePrEP_HIGH"),
  stratify_columns = c("Year", "Gender", "Age", "IP_Key.Risk"),
  min_age_inclusive = 0,
  max_age_inclusive = 99
)


```

## Scale by population scaling factor
```{r Scale by Population Scaling Factor}
CENSUS_YEAR = 2010
ZWE_CENSUS_POP = 12696893 # WPP data

sim.results.pop.scaling <- sim.results.base %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = ZWE_CENSUS_POP/total.pop)

sim.results.base <- sim.results.base %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )


sim.results.pop.scaling <- sim.results.prep %>% 
      filter(Year == CENSUS_YEAR) %>%
      group_by(sim.id) %>%
      summarize(total.pop = sum(Population), .groups = 'keep') %>% 
      mutate(pop.scaling.factor = ZWE_CENSUS_POP/total.pop)

sim.results.prep <- sim.results.prep %>% 
  inner_join(
    sim.results.pop.scaling,
    by = c("sim.id")
  )



```

```{r}
nruns = sim.results.base$sim.ix %>% unique %>% length()

nruns
```


# Compare results to calibration targets

## Prevalence plots

```{r Prevalence calibration targets}
zwe.phia = data.frame(
  Year = c(2016, 2016),
  Gender = c("Male", "Female"),
  mean.prev= c(12, 16),
  lower = c(11.1, 15.3),
  upper = c(12.8,16.8)
)
zwe.dhs = data.frame(
  Year = c(2006, 2010, 2015, 2006, 2010, 2015),
  Gender = c("Male", "Male", "Male", "Female", "Female", "Female"),
  mean.prev = c(14.5, 12.3, 10.5, 21.1, 17.7, 16.7),
  lower = c(13.2, 11.3, 9.5, 19.6, 16.6, 15.5),
  upper = c(15.9, 13.3, 11.5, 22.6, 18.8, 17.8)
)
 
prev.target <- rbind(zwe.phia, zwe.dhs) %>% arrange(Year, Gender)
```

```{r Prevalence}
p <- EMODAnalyzeR::emodplot.prevalence(
      #sim.results.base %>% filter(Age >= 15, Age < 50),
      sim.results.prep %>% filter(Age >= 15, Age < 50),
  date.start = 1990,
  date.end = 2020
)

p +
  geom_errorbar(data = prev.target,
             mapping = aes(x = Year, ymin = lower/100, ymax = upper/100)) + 
  facet_wrap(~ Gender, ncol=2)
```

```{r Prevalence by Age}

# Read in the calibration targets data
prev.target <- read_csv("/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/Analysis/zwe_age_prevalence_data.csv")

# Convenient relabels of age bins
prev.target$Age = factor(prev.target$AgeBin, 
                         levels = c("[0:5)", "[5:10)", "[10:15)", "[15:20)", "[20:25)", "[25:30)", "[30:35)", "[35:40)", "[40:45)", "[45:50)", "[50:55)", "[55:60)", "[60:65)"),
                         labels = c(1:13)
                         )

prev.target$Year.label = factor(prev.target$Year, 
                          levels = c(2006.0, 2011.0, 2015.0, 2016),
                          labels = c( "2006 (DHS)","2011 (DHS)", "2015 (DHS)", "2016 (PHIA)"))

#head(prev.target)

```

```{r}
age_bins = c(0,5,10,15,20,25,30,35,40,45,50,55,60,65)
age_labels = c()
for (i in 1:(length(age_bins) - 1)){
  age_labels <- append(age_labels, paste0("[",age_bins[i],":",age_bins[i + 1],")"))
}

subset_years = c(2006.0, 2011.0, 2015.0, 2016)

data <- sim.results.prep %>% 
  select(Year, Age, Gender, sim.id, Infected, Population) %>% 
  filter(Year %in% subset_years) %>% 
  mutate(AgeBin = cut(Age, breaks = age_bins, right = FALSE)) %>% 
  group_by(Year, AgeBin, Gender, sim.id) %>% 
  summarize(Infected = sum(Infected), Population = sum(Population)) %>% ungroup() %>% 
  mutate(Prevalence = Infected/Population)

data.mean <-  data %>% 
  group_by(Year, AgeBin, Gender) %>% 
  summarize(Prevalence = mean(Prevalence), .groups = 'keep')  %>% 
  ungroup() %>% 
  mutate(Gender = case_when(Gender==0 ~ "Male", Gender==1 ~ "Female"))
data.mean$AgeBin_index = factor(data.mean$AgeBin,labels = 1:length(age_labels))

ggplot() + 
  geom_point(data.mean, mapping = aes(x = AgeBin_index, y = Prevalence), color = 'blue') + 
  geom_point(data = prev.target, 
             mapping = aes(x = Age, y = Prevalence)) + 
  geom_errorbar(data = prev.target,
                mapping = aes(x = Age, ymin = lower, ymax = upper)) +
  facet_grid(cols = vars(Gender), rows = vars(Year)) 

```

## ART Plots

```{r}
xl.path = "/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/Data/calibration_ingest_form_ZWE_2022-07-15.xlsm"
obs.onart.sheet <- EMODAnalyzeR::read.ingest.sheet(xl.path, sheet = 'Obs-OnART')
```


```{r}
data <- sim.results.prep %>% 
    group_by(Year, Gender, sim.id, scenario_name) %>% 
    summarize(On_ART = sum(On_ART*pop.scaling.factor), 
              Population = sum(Population*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup()

p <- EMODAnalyzeR::emodplot.by_gender(data, 1990, 2040, 'On_ART', title="ART") 

p + 
  geom_point(data = obs.onart.sheet %>% filter(Province == "All", AgeBin == '[15:100)') %>% 
    group_by(Year, Gender) %>% 
    summarize(OnART = sum(OnART), .groups = 'keep'),
    mapping= aes(x = Year, y = OnART))
```


# Extract Results for MIHPSA

## HIV Incidence

### PrEP

```{r Incidence - prep}
# Males 15-49
p1 <- sim.results.prep %>% 
  filter(Gender == 0, Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  mutate(incidence = 100 * incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_M1549_sd = sd(incidence),
            HIVIncid_M1549_M = mean(incidence), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_M1549_95LL = lower_ci(HIVIncid_M1549_M, HIVIncid_M1549_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVIncid_M1549_95UL = upper_ci(HIVIncid_M1549_M, HIVIncid_M1549_sd/sqrt(nruns), nruns, conf_level = .95)
    ) %>% select(-HIVIncid_M1549_sd)

# Females 15-49
p2 <- sim.results.prep %>% 
  filter(Gender == 1, Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  mutate(incidence = 100 * incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_F1549_sd = sd(incidence),
            HIVIncid_F1549_M = mean(incidence), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_F1549_95LL = lower_ci(HIVIncid_F1549_M, HIVIncid_F1549_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVIncid_F1549_95UL = upper_ci(HIVIncid_F1549_M, HIVIncid_F1549_sd/sqrt(nruns), nruns, conf_level = .95)
    ) %>% select(-HIVIncid_F1549_sd)

# Adults 15-49
p3 <- sim.results.prep %>% 
  filter(Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_A1549_sd = sd(incidence),
            HIVIncid_A1549_M = mean(incidence), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_A1549_95LL = lower_ci(HIVIncid_A1549_M, HIVIncid_A1549_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVIncid_A1549_95UL = upper_ci(HIVIncid_A1549_M, HIVIncid_A1549_sd/sqrt(nruns), nruns, conf_level = .95)
    ) %>% select(-HIVIncid_A1549_sd)

# Females 15-24
p4 <- sim.results.prep %>% 
  filter(Gender == 1, Age >=15, Age < 25) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_F1524_sd = sd(incidence), 
            HIVIncid_F1524_M = mean(incidence),  .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_F1524_95LL = lower_ci(HIVIncid_F1524_M, HIVIncid_F1524_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVIncid_F1524_95UL = upper_ci(HIVIncid_F1524_M, HIVIncid_F1524_sd/sqrt(nruns), nruns, conf_level = .95)
    ) %>% select(-HIVIncid_F1524_sd)

# FSW ages >15
p5 <- sim.results.prep %>% 
  filter(Gender == 1, Age >= 15, IP_Key.Risk == "HIGH") %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_FSW1599_sd = sd(incidence),
            HIVIncid_FSW1599_M = mean(incidence),  .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_FSW1599_95LL = lower_ci(HIVIncid_FSW1599_M, HIVIncid_FSW1599_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVIncid_FSW1599_95UL = upper_ci(HIVIncid_FSW1599_M, HIVIncid_FSW1599_sd/sqrt(nruns), nruns, conf_level = .95)
    ) %>% select(-HIVIncid_FSW1599_sd)

inc.prep.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  mutate(Year = floor(Year)) 

# inc.prep.summary %>% 
#   pivot_longer(-Year) %>% 
#   pivot_wider(names_from = Year, values_from = value)


ggplot(data = inc.prep.summary) + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_M1549_M), color = 'blue') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_F1549_M), color = 'green') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_A1549_M), color = 'purple') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_F1524_M), color = 'black') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_FSW1599_M), color = 'red')

```


### Essential

```{r Incidence}
# Males 15-49
p1 <- sim.results.base %>% 
  filter(Gender == 0, Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  mutate(incidence = 100 * incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_M1549_sd = sd(incidence),
            HIVIncid_M1549_M = mean(incidence), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_M1549_95LL = lower_ci(HIVIncid_M1549_M, HIVIncid_M1549_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVIncid_M1549_95UL = upper_ci(HIVIncid_M1549_M, HIVIncid_M1549_sd/sqrt(nruns), nruns, conf_level = .95)
    ) %>% select(-HIVIncid_M1549_sd)

# Females 15-49
p2 <- sim.results.base %>% 
  filter(Gender == 1, Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  mutate(incidence = 100 * incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_F1549_sd = sd(incidence),
            HIVIncid_F1549_M = mean(incidence), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_F1549_95LL = lower_ci(HIVIncid_F1549_M, HIVIncid_F1549_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVIncid_F1549_95UL = upper_ci(HIVIncid_F1549_M, HIVIncid_F1549_sd/sqrt(nruns), nruns, conf_level = .95)
    ) %>% select(-HIVIncid_F1549_sd)

# Adults 15-49
p3 <- sim.results.base %>% 
  filter(Age >=15, Age < 50) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_A1549_sd = sd(incidence),
            HIVIncid_A1549_M = mean(incidence), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_A1549_95LL = lower_ci(HIVIncid_A1549_M, HIVIncid_A1549_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVIncid_A1549_95UL = upper_ci(HIVIncid_A1549_M, HIVIncid_A1549_sd/sqrt(nruns), nruns, conf_level = .95)
    ) %>% select(-HIVIncid_A1549_sd)

# Females 15-24
p4 <- sim.results.base %>% 
  filter(Gender == 1, Age >=15, Age < 25) %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_F1524_sd = sd(incidence), 
            HIVIncid_F1524_M = mean(incidence),  .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_F1524_95LL = lower_ci(HIVIncid_F1524_M, HIVIncid_F1524_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVIncid_F1524_95UL = upper_ci(HIVIncid_F1524_M, HIVIncid_F1524_sd/sqrt(nruns), nruns, conf_level = .95)
    ) %>% select(-HIVIncid_F1524_sd)

# FSW ages >15
p5 <- sim.results.base %>% 
  filter(Gender == 1, Age >= 15, IP_Key.Risk == "HIGH") %>% 
  EMODAnalyzeR::calculate.incidence() %>% 
  mutate(incidence = 100 * incidence) %>% 
  dplyr::select(Year, Gender, sim.id, incidence) %>% 
  group_by(Year) %>% 
  summarize(HIVIncid_FSW1599_sd = sd(incidence),
            HIVIncid_FSW1599_M = mean(incidence),  .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVIncid_FSW1599_95LL = lower_ci(HIVIncid_FSW1599_M, HIVIncid_FSW1599_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVIncid_FSW1599_95UL = upper_ci(HIVIncid_FSW1599_M, HIVIncid_FSW1599_sd/sqrt(nruns), nruns, conf_level = .95)
    ) %>% select(-HIVIncid_FSW1599_sd)

inc.base.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  mutate(Year = floor(Year)) 

# inc.base.summary %>% 
#   pivot_longer(-Year) %>% 
#   pivot_wider(names_from = Year, values_from = value)

ggplot(data = inc.base.summary) + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_M1549_M), color = 'blue') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_F1549_M), color = 'green') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_A1549_M), color = 'purple') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_F1524_M), color = 'black') + 
  geom_line(mapping = aes(x = Year, y = HIVIncid_FSW1599_M), color = 'red')

```

## Oral PrEP for AGYW

### PrEP

```{r}
# Number of AGYW who used oral TDF in the last year
p1 <- sim.results.prep %>% 
  filter(Gender == 1, Age >=15, Age < 25) %>% 
  dplyr::select(Year, sim.id, ReceivePrEP_HIGH, pop.scaling.factor) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NTDFPrEP_F1524_M = sum(ReceivePrEP_HIGH*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NTDFPrEP_F1524_M = mean(NTDFPrEP_F1524_M), .groups = 'keep') %>% 
  ungroup()

# Number of FSWs who used oral TDF in the last year
p2 <- sim.results.prep %>% 
  filter(Gender == 1, Age >=15, IP_Key.Risk == 'HIGH') %>% 
  dplyr::select(Year, sim.id, ReceivePrEP_HIGH, pop.scaling.factor) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NTDFPrEP_FSW1599_M = sum(ReceivePrEP_HIGH*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NTDFPrEP_FSW1599_M = mean(NTDFPrEP_FSW1599_M), .groups = 'keep') %>% 
  ungroup()

# Number AGYW at elevated risk
p3 <- sim.results.prep %>% 
  filter(Gender == 1, Age >= 15, Age <25, IP_Key.Risk == 'HIGH') %>% 
  dplyr::select(Year, sim.id, Population, pop.scaling.factor) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NAlive_ElevRiskF1524_M = sum(Population*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_ElevRiskF1524_M = mean(NAlive_ElevRiskF1524_M), .groups = 'keep') %>% 
  ungroup()

# % AGYW at high risk on prep
p4 <- sim.results.prep %>% 
  filter(Gender == 1, Age >= 15, Age <25, IP_Key.Risk == 'HIGH') %>% 
  dplyr::select(Year, sim.id, Population, ReceivePrEP_HIGH) %>% 
  group_by(Year, sim.id) %>% 
  summarize(onprep = sum(ReceivePrEP_HIGH), 
            pop = sum(Population), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(P_TDFPrEP_ElevRiskF1524_M = 100*mean(onprep/pop), .groups = 'keep') %>% 
  ungroup()

prep.prep.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  mutate(Year = floor(Year)) 

ggplot(data = prep.prep.summary) + 
  geom_line(mapping = aes(x = Year, y = NTDFPrEP_F1524_M), color = 'green') + 
  geom_line(mapping = aes(x = Year, y = NTDFPrEP_FSW1599_M), color = 'purple') + 
  geom_line(mapping = aes(x = Year, y = NAlive_ElevRiskF1524_M), color = 'black')
  #geom_line(mapping = aes(x = Year, y = P_TDFPrEP_ElevRiskF1524_M), color = 'red')
```

### Essential

```{r}
# Number of AGYW who used oral TDF in the last year
p1 <- sim.results.base %>% 
  filter(Gender == 1, Age >=15, Age < 25) %>% 
  dplyr::select(Year, sim.id, ReceivePrEP_HIGH, pop.scaling.factor) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NTDFPrEP_F1524_M = sum(ReceivePrEP_HIGH*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NTDFPrEP_F1524_M = mean(NTDFPrEP_F1524_M), .groups = 'keep') %>% 
  ungroup()

# Number of FSWs who used oral TDF in the last year
p2 <- sim.results.base %>% 
  filter(Gender == 1, Age >=15, IP_Key.Risk == 'HIGH') %>% 
  dplyr::select(Year, sim.id, ReceivePrEP_HIGH, pop.scaling.factor) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NTDFPrEP_FSW1599_M = sum(ReceivePrEP_HIGH*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NTDFPrEP_FSW1599_M = mean(NTDFPrEP_FSW1599_M), .groups = 'keep') %>% 
  ungroup()

# Number AGYW at elevated risk
p3 <- sim.results.base %>% 
  filter(Gender == 1, Age >= 15, Age <25, IP_Key.Risk == 'HIGH') %>% 
  dplyr::select(Year, sim.id, Population, pop.scaling.factor) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NAlive_ElevRiskF1524_M = sum(Population*pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_ElevRiskF1524_M = mean(NAlive_ElevRiskF1524_M), .groups = 'keep') %>% 
  ungroup()

# % AGYW at high risk on prep
p4 <- sim.results.base %>% 
  filter(Gender == 1, Age >= 15, Age <25, IP_Key.Risk == 'HIGH') %>% 
  dplyr::select(Year, sim.id, Population, ReceivePrEP_HIGH) %>% 
  group_by(Year, sim.id) %>% 
  summarize(onprep = sum(ReceivePrEP_HIGH), 
            pop = sum(Population), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(P_TDFPrEP_ElevRiskF1524_M = 100*mean(onprep/pop), .groups = 'keep') %>% 
  ungroup()

prep.base.summary <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  mutate(Year = floor(Year)) 

ggplot(data = prep.base.summary) + 
  geom_line(mapping = aes(x = Year, y = NTDFPrEP_F1524_M), color = 'green') + 
  geom_line(mapping = aes(x = Year, y = NTDFPrEP_FSW1599_M), color = 'purple') + 
  geom_line(mapping = aes(x = Year, y = NAlive_ElevRiskF1524_M), color = 'black')
  #geom_line(mapping = aes(x = Year, y = P_TDFPrEP_ElevRiskF1524_M), color = 'red')
```

## YLDs - current categories

Use the assumption that other people are using: that 1/8 of the people who have CD4 under 200 have CD4 under 50

### PrEP
```{r}
# check: how do we sum up the total number of infected people, or infected people on art

# sim.results.prep %>% 
#   filter(Year == 2010) %>% 
#   dplyr::select(Year, Population, Infected, On_ART, 
#                 Infected.CD4.Under.200..Not.On.ART., Infected.CD4.200.To.349..Not.On.ART.,
#                 Infected.CD4.350.To.499..Not.On.ART., Infected.CD4.500.Plus..Not.On.ART.
#                 ) %>% 
#   group_by(Year) %>% 
#   summarize(Population = sum(Population),
#             Infected = sum(Infected),
#             On_ART = sum(On_ART),
#             Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.),
#             Infected.CD4.200.To.349..Not.On.ART. = sum(Infected.CD4.200.To.349..Not.On.ART.),
#             Infected.CD4.350.To.499..Not.On.ART. = sum(Infected.CD4.350.To.499..Not.On.ART.),
#             Infected.CD4.500.Plus..Not.On.ART. = sum(Infected.CD4.500.Plus..Not.On.ART.),
#             .groups = 'keep') %>% 
#   pivot_longer( cols = c("Population", "Infected", "On_ART",
#                          "Infected.CD4.Under.200..Not.On.ART.",
#                          "Infected.CD4.200.To.349..Not.On.ART.",
#                          "Infected.CD4.350.To.499..Not.On.ART.",
#                          "Infected.CD4.500.Plus..Not.On.ART."))
```


```{r}
# Number of 15+ PLHIV not on treatment, with CD4 >= 500
# NHIV_A1599_NoART_CD4500pl_M
p1 <- sim.results.prep %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.500.Plus..Not.On.ART. = sum(Infected.CD4.500.Plus..Not.On.ART. * pop.scaling.factor), 
            .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD4500pl_M = mean(Infected.CD4.500.Plus..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 350 <= CD4 < 500
#NHIV_A1599_NoART_CD4350499_M
p2 <- sim.results.prep %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.350.To.499..Not.On.ART. = sum(Infected.CD4.350.To.499..Not.On.ART.* pop.scaling.factor ), 
            .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD4350499_M = mean(Infected.CD4.350.To.499..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 200 <= CD4 < 350
# NHIV_A1599_NoART_CD4200349_M
p3  <- sim.results.prep %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.200.To.349..Not.On.ART. = sum(Infected.CD4.200.To.349..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD4200349_M = mean(Infected.CD4.200.To.349..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 50 <= CD4 < 200
# NHIV_A1599_NoART_CD450199_M
p4a  <- sim.results.prep %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor)*7/8, .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD450199_M = mean(Infected.CD4.Under.200..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 0 <= CD4 < 50
# NHIV_A1599_NoART_CD4050_M
p4b  <- sim.results.prep %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor)/8, .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD4050_M = mean(Infected.CD4.Under.200..Not.On.ART.))


# Number of 0-14yo PLHIV not on treatment, with CD4 >= 500
# NHIV_A014_NoART_CD4500pl_M
p5 <- sim.results.prep %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.500.Plus..Not.On.ART. = sum(Infected.CD4.500.Plus..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD4500pl_M = mean(Infected.CD4.500.Plus..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 350 <= CD4 < 500
# NHIV_A014_NoART_CD4350499_M
p6 <- sim.results.prep %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.200.To.349..Not.On.ART. = sum(Infected.CD4.200.To.349..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD4350499_M = mean(Infected.CD4.200.To.349..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 200 <= CD4 < 350
# NHIV_A014_NoART_CD4200349_M
p7 <- sim.results.prep %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.350.To.499..Not.On.ART. = sum(Infected.CD4.350.To.499..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD4200349_M = mean(Infected.CD4.350.To.499..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 0 <= CD4 < 200
# NHIV_A014_NoART_CD450199_M
p8a <- sim.results.prep %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor)*7/8, .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD450199_M = mean(Infected.CD4.Under.200..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 0 <= CD4 < 200
# NHIV_A014_NoART_CD4050_M
p8b <- sim.results.prep %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor)/8, .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD4050_M = mean(Infected.CD4.Under.200..Not.On.ART.))

ylds.current.prep <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4a, by = 'Year') %>%
  merge(p4b, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  merge(p6, by = 'Year') %>%
  merge(p7, by = 'Year') %>%
  merge(p8a, by = 'Year') %>%
  merge(p8b, by = 'Year') %>%
  mutate(Year = floor(Year)) 
```

### Essential

```{r}
# Number of 15+ PLHIV not on treatment, with CD4 >= 500
# NHIV_A1599_NoART_CD4500pl_M
p1 <- sim.results.base %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.500.Plus..Not.On.ART. = sum(Infected.CD4.500.Plus..Not.On.ART. * pop.scaling.factor), 
            .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD4500pl_M = mean(Infected.CD4.500.Plus..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 350 <= CD4 < 500
#NHIV_A1599_NoART_CD4350499_M
p2 <- sim.results.base %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.350.To.499..Not.On.ART. = sum(Infected.CD4.350.To.499..Not.On.ART.* pop.scaling.factor ), 
            .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD4350499_M = mean(Infected.CD4.350.To.499..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 200 <= CD4 < 350
# NHIV_A1599_NoART_CD4200349_M
p3  <- sim.results.base %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.200.To.349..Not.On.ART. = sum(Infected.CD4.200.To.349..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD4200349_M = mean(Infected.CD4.200.To.349..Not.On.ART.))

# Number of 15+ PLHIV not on treatment, with 0 <= CD4 < 200
# NHIV_A1599_NoART_CD450199_M
p4  <- sim.results.base %>% 
  filter(Age >= 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A1599_NoART_CD450199_M = mean(Infected.CD4.Under.200..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with CD4 >= 500
# NHIV_A014_NoART_CD4500pl_M
p5 <- sim.results.base %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.500.Plus..Not.On.ART. = sum(Infected.CD4.500.Plus..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD4500pl_M = mean(Infected.CD4.500.Plus..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 350 <= CD4 < 500
# NHIV_A014_NoART_CD4350499_M
p6 <- sim.results.base %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.200.To.349..Not.On.ART. = sum(Infected.CD4.200.To.349..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD4350499_M = mean(Infected.CD4.200.To.349..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 200 <= CD4 < 350
# NHIV_A014_NoART_CD4200349_M
p7 <- sim.results.base %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.350.To.499..Not.On.ART. = sum(Infected.CD4.350.To.499..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD4200349_M = mean(Infected.CD4.350.To.499..Not.On.ART.))

# Number of 0-14yo PLHIV not on treatment, with 0 <= CD4 < 200
# NHIV_A014_NoART_CD450199_M
p8 <- sim.results.base %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(Infected.CD4.Under.200..Not.On.ART. = sum(Infected.CD4.Under.200..Not.On.ART.* pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_NoART_CD450199_M = mean(Infected.CD4.Under.200..Not.On.ART.))

ylds.current.base <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  merge(p6, by = 'Year') %>%
  merge(p7, by = 'Year') %>%
  merge(p8, by = 'Year') %>%
  mutate(Year = floor(Year)) 
```
## YLDs - new categories

```{r}
# Asymptomatic, Undiagnosed

# Asymptomatic, Diagnosed, not on ART

# Asymptomatic, Diagnosed, on ART

# Symptomatic, not AIDS

# Symptomatic, AIDS
```

## YLLs

For all individuals who died from HIV at age X, find the correct life expectancy for that individual
Then sum up the difference between the age of death and the life expectancy

```{r Load Life Expectancy Tables}

xl.path <- "/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/Analysis/YLL_Tables.xlsx"

le.table.undisc <- readxl::read_excel(xl.path, sheet = "Undiscounted", range = "A1:C93", col_names = TRUE)
colnames(le.table.undisc) <- c("Age", 1, 0)
le.table.undisc <- pivot_longer(
  le.table.undisc, 
  cols = c(`0`,`1`),
  names_to = c("Gender"),
  values_to = "YLL")
```


### PrEP


```{r}
# Future YLL incurred at calendar year of death for adults aged 15+

# aggregate up the number of HIV related deaths for each age group

data.yll <- sim.results.prep %>% 
  dplyr::select(Year, Age, Gender, Died_from_HIV, sim.id, pop.scaling.factor) %>% 
  group_by(Year, Gender, Age, sim.id) %>% 
  # count total number of people who have died from HIV, 
  # for each year, age, gender and simulation
  summarize(Died_from_HIV = sum(Died_from_HIV*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  # merge with YLL table
  merge(le.table.undisc, 
        by = c("Age", "Gender"))

yll.adults <- data.yll  %>%   
  # subset on adults
  filter(Age >= 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_A1599_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()


yll.children <- data.yll  %>%   
  # subset on children
  filter(Age < 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_A014_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()
  
discount.percent = .03
discount_start_year = 2024

yll.adults.disc <- data.yll  %>%   
  # subset on adults
  filter(Age >= 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # calculate discount factor
  mutate(discount.factor = case_when(Year <= 2024 ~ 1,
                                     Year > 2024 ~ (1 - discount.percent)^(Year - discount_start_year))) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs * discount.factor), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_3Disc_A1599_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()


yll.children.disc <- data.yll  %>%   
  # subset on adults
  filter(Age < 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # calculate discount factor
  mutate(discount.factor = case_when(Year <= 2024 ~ 1,
                                     Year > 2024 ~ (1 - discount.percent)^(Year - discount_start_year))) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs * discount.factor), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_3Disc_A014_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()


ylls.current.prep <- merge(yll.adults, yll.children, by = 'Year') %>% 
  merge(yll.adults.disc, by = 'Year') %>% 
  merge(yll.children.disc, by = 'Year')
```

### Essential

```{r}
# Future YLL incurred at calendar year of death for adults aged 15+

# aggregate up the number of HIV related deaths for each age group

data.yll.base <- sim.results.base %>% 
  dplyr::select(Year, Age, Gender, Died_from_HIV, sim.id, pop.scaling.factor) %>% 
  group_by(Year, Gender, Age, sim.id) %>% 
  # count total number of people who have died from HIV, 
  # for each year, age, gender and simulation
  summarize(Died_from_HIV = sum(Died_from_HIV*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  # merge with YLL table
  merge(le.table.undisc, 
        by = c("Age", "Gender"))

yll.adults <- data.yll.base  %>%   
  # subset on adults
  filter(Age >= 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_A1599_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()


yll.children <- data.yll.base  %>%   
  # subset on children
  filter(Age < 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_A014_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()
  
discount.percent = .03
discount_start_year = 2024

yll.adults.disc <- data.yll.base  %>%   
  # subset on adults
  filter(Age >= 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # calculate discount factor
  mutate(discount.factor = case_when(Year <= 2024 ~ 1,
                                     Year > 2024 ~ (1 - discount.percent)^(Year - discount_start_year))) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs * discount.factor), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_3Disc_A1599_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()


yll.children.disc <- data.yll.base  %>%   
  # subset on adults
  filter(Age < 15) %>% 
  # calculate total YLLs for each year/age/gender group
  mutate(total.YLLs = Died_from_HIV * YLL) %>% 
  # calculate discount factor
  mutate(discount.factor = case_when(Year <= 2024 ~ 1,
                                     Year > 2024 ~ (1 - discount.percent)^(Year - discount_start_year))) %>% 
  # sum YLLs across age/gender
  group_by(Year, sim.id) %>% 
  summarize(total.YLLs = sum(total.YLLs * discount.factor), .groups = 'keep') %>% 
  # average YLLs across simulation runs
  group_by(Year) %>%
  summarize(YLL_AgeGenLifeExpect_3Disc_A014_M = mean(total.YLLs), .groups = 'keep') %>% ungroup()


ylls.current.base <- merge(yll.adults, yll.children, by = 'Year') %>% 
  merge(yll.adults.disc, by = 'Year') %>% 
  merge(yll.children.disc, by = 'Year')
```


## ART 

### PrEP Scenario

Number of Adults and children on ART

```{r}
# NOnART_M1599_M
# number of males on art, age 15-99
p1 <- sim.results.prep %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NOnART_M1599_M = sum(On_ART * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NOnART_M1599_M_sd = sd(NOnART_M1599_M), 
            NOnART_M1599_M = mean(NOnART_M1599_M), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NOnART_M1599_95LL = lower_ci(NOnART_M1599_M, NOnART_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NOnART_M1599_95UL = upper_ci(NOnART_M1599_M, NOnART_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% select(-NOnART_M1599_M_sd)

# Number Female adults on ART
# NOnART_F1599_M
p2 <- sim.results.prep %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NOnART_F1599_M = sum(On_ART  * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NOnART_F1599_M_sd = sd(NOnART_F1599_M), 
            NOnART_F1599_M = mean(NOnART_F1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NOnART_F1599_95LL = lower_ci(NOnART_F1599_M, NOnART_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NOnART_F1599_95UL = upper_ci(NOnART_F1599_M, NOnART_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% select(-NOnART_F1599_M_sd)

# Number adolescents on ART 
# NOnART_A1524_M
p3 <- sim.results.prep %>% 
  filter(Age >=15, Age <25) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NOnART_A1524_M = sum(On_ART  * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NOnART_A1524_M_sd = sd(NOnART_A1524_M), 
            NOnART_A1524_M = mean(NOnART_A1524_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NOnART_A1524_95LL = lower_ci(NOnART_A1524_M, NOnART_A1524_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NOnART_A1524_95UL = upper_ci(NOnART_A1524_M, NOnART_A1524_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% select(-NOnART_A1524_M_sd)

# Number adults on ART
# NOnART_A099_M
p4 <- sim.results.prep %>% 
  filter(Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NOnART_A099_M = sum(On_ART  * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NOnART_A099_M_sd = sd(NOnART_A099_M), 
            NOnART_A099_M = mean(NOnART_A099_M), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NOnART_A099_95LL = lower_ci(NOnART_A099_M, NOnART_A099_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NOnART_A099_95UL = upper_ci(NOnART_A099_M, NOnART_A099_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% select(-NOnART_A099_M_sd)

# Number children on ART
# NOnART_A014_M
p5 <- sim.results.prep %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NOnART_A014_M = sum(On_ART  * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NOnART_A014_M_sd = sd(NOnART_A014_M), 
            NOnART_A014_M = mean(NOnART_A014_M), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NOnART_A014_95LL = lower_ci(NOnART_A014_M, NOnART_A014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NOnART_A014_95UL = upper_ci(NOnART_A014_M, NOnART_A014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% select(-NOnART_A014_M_sd)

NOnART.current.prep <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  mutate(Year = floor(Year)) 

```

Percent on ART

```{r}
# Percent of HIV positive males on art, age 15-99
# P_onART_HIVM1599_M
p1 <- sim.results.prep %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(OnART = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected * pop.scaling.factor) , .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(P_onART = case_when(PLHIV > 0 ~ 100*OnART/PLHIV,
                             PLHIV == 0 ~ 0)) %>% 
  group_by(Year) %>% 
  summarize(P_onART_HIVM1599_M_sd = sd(P_onART), 
            P_onART_HIVM1599_M = mean(P_onART), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_HIVM1599_95LL = lower_ci(P_onART_HIVM1599_M, P_onART_HIVM1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_HIVM1599_95UL = upper_ci(P_onART_HIVM1599_M, P_onART_HIVM1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_onART_HIVM1599_M_sd)

# Percent of HIV positive Female adults on ART, age 15-99
# P_onART_HIVF1599_M
p2 <- sim.results.prep %>% 
  filter(Gender == 1, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(OnART = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected * pop.scaling.factor) , .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(P_onART = case_when(PLHIV > 0 ~ 100* OnART/PLHIV,
                             PLHIV == 0 ~ 0)) %>%
  group_by(Year) %>% 
  summarize(P_onART_HIVF1599_M_sd = sd(P_onART), 
            P_onART_HIVF1599_M = mean(P_onART), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_HIVF1599_95LL = lower_ci(P_onART_HIVF1599_M, P_onART_HIVF1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_HIVF1599_95UL = upper_ci(P_onART_HIVF1599_M, P_onART_HIVF1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  )%>% 
  select(-P_onART_HIVF1599_M_sd)

# Percent HIV positive females 15-24 on ART
# P_onART_HIVF1524_M
p3 <- sim.results.prep %>% 
  filter(Gender == 1, Age >=15, Age <25) %>% 
  group_by(Year, sim.id) %>% 
  summarize(OnART = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected * pop.scaling.factor) , .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(P_onART = case_when(PLHIV > 0 ~ 100* OnART/PLHIV,
                             PLHIV == 0 ~ 0)) %>%
  group_by(Year) %>% 
  summarize(P_onART_HIVF1524_M = mean(P_onART), 
            .groups = 'keep') %>% 
  ungroup()

# percent hiv positive individuals 15-24 on ART
# P_onART_HIVA1524_M
p4 <- sim.results.prep %>% 
  filter(Age >=15, Age <25) %>% 
  group_by(Year, sim.id) %>% 
  summarize(OnART = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected * pop.scaling.factor) , .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(P_onART = case_when(PLHIV > 0 ~ 100* OnART/PLHIV,
                             PLHIV == 0 ~ 0)) %>%
  group_by(Year) %>% 
  summarize(P_onART_HIVA1524_M = mean(P_onART), 
            .groups = 'keep') %>% 
  ungroup()

# percent hiv positive adults on ART
# P_onART_HIVA1599_M
p5 <- sim.results.prep %>% 
  filter(Age >=15, Age <25) %>% 
  group_by(Year, sim.id) %>% 
  summarize(OnART = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected * pop.scaling.factor) , .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(P_onART = case_when(PLHIV > 0 ~ 100* OnART/PLHIV,
                             PLHIV == 0 ~ 0)) %>%
  group_by(Year) %>% 
  summarize(P_onART_HIVA1599_M_sd = sd(P_onART), 
            P_onART_HIVA1599_M = mean(P_onART), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_HIVA1599_95LL = lower_ci(P_onART_HIVA1599_M, P_onART_HIVA1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_HIVA1599_95UL = upper_ci(P_onART_HIVA1599_M, P_onART_HIVA1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_onART_HIVA1599_M_sd)

# Percent HIV positive children on ART
# P_onART_HIVA014_M
p6 <- sim.results.prep %>% 
  filter(Age >=15, Age <25) %>% 
  group_by(Year, sim.id) %>% 
  summarize(OnART = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected * pop.scaling.factor) , .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(P_onART = case_when(PLHIV > 0 ~ 100* OnART/PLHIV,
                             PLHIV == 0 ~ 0)) %>%
  group_by(Year) %>% 
  summarize(P_onART_HIVA014_M_sd = sd(P_onART), 
            P_onART_HIVA014_M = mean(P_onART), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_HIVA014_95LL = lower_ci(P_onART_HIVA014_M, P_onART_HIVA014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_HIVA014_95UL = upper_ci(P_onART_HIVA014_M, P_onART_HIVA014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_onART_HIVA014_M_sd)

# Percent of HIV positive FSW ages 15+ who are on ART
# P_onART_HIVFSW1599_M
p7 <- sim.results.prep %>% 
  filter(Gender == 1, Age >=15, IP_Key.Risk == "HIGH") %>% 
  group_by(Year, sim.id) %>% 
  summarize(OnART = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected * pop.scaling.factor) , .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(P_onART = case_when(PLHIV > 0 ~ 100* OnART/PLHIV,
                             PLHIV == 0 ~ 0)) %>%
  group_by(Year) %>% 
  summarize(P_onART_HIVFSW1599_M = mean(P_onART), 
            .groups = 'keep') %>% 
  ungroup()

P_onART.current.prep <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  merge(p6, by = 'Year') %>%
  merge(p7, by = 'Year') %>%
  mutate(Year = floor(Year)) 

```

### Essential Scenario

```{r}
# NOnART_M1599_M
# number of males on art, age 15-99
p1 <- sim.results.base %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NOnART_M1599_M = sum(On_ART * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NOnART_M1599_M_sd = sd(NOnART_M1599_M), 
            NOnART_M1599_M = mean(NOnART_M1599_M), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NOnART_M1599_95LL = lower_ci(NOnART_M1599_M, NOnART_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NOnART_M1599_95UL = upper_ci(NOnART_M1599_M, NOnART_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% select(-NOnART_M1599_M_sd)

# Number Female adults on ART
# NOnART_F1599_M
p2 <- sim.results.base %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NOnART_F1599_M = sum(On_ART  * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NOnART_F1599_M_sd = sd(NOnART_F1599_M), 
            NOnART_F1599_M = mean(NOnART_F1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NOnART_F1599_95LL = lower_ci(NOnART_F1599_M, NOnART_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NOnART_F1599_95UL = upper_ci(NOnART_F1599_M, NOnART_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% select(-NOnART_F1599_M_sd)

# Number adolescents on ART 
# NOnART_A1524_M
p3 <- sim.results.base %>% 
  filter(Age >=15, Age <25) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NOnART_A1524_M = sum(On_ART  * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NOnART_A1524_M_sd = sd(NOnART_A1524_M), 
            NOnART_A1524_M = mean(NOnART_A1524_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NOnART_A1524_95LL = lower_ci(NOnART_A1524_M, NOnART_A1524_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NOnART_A1524_95UL = upper_ci(NOnART_A1524_M, NOnART_A1524_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% select(-NOnART_A1524_M_sd)

# Number adults on ART
# NOnART_A099_M
p4 <- sim.results.base %>% 
  filter(Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NOnART_A099_M = sum(On_ART  * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NOnART_A099_M_sd = sd(NOnART_A099_M), 
            NOnART_A099_M = mean(NOnART_A099_M), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NOnART_A099_95LL = lower_ci(NOnART_A099_M, NOnART_A099_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NOnART_A099_95UL = upper_ci(NOnART_A099_M, NOnART_A099_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% select(-NOnART_A099_M_sd)

# Number children on ART
# NOnART_A014_M
p5 <- sim.results.base %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(NOnART_A014_M = sum(On_ART  * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NOnART_A014_M_sd = sd(NOnART_A014_M), 
            NOnART_A014_M = mean(NOnART_A014_M), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NOnART_A014_95LL = lower_ci(NOnART_A014_M, NOnART_A014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NOnART_A014_95UL = upper_ci(NOnART_A014_M, NOnART_A014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% select(-NOnART_A014_M_sd)

NOnART.current.base <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  mutate(Year = floor(Year)) 

```

Percent of PLHIV on ART

```{r}
# Percent of HIV positive males on art, age 15-99
# P_onART_HIVM1599_M
p1 <- sim.results.base %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(OnART = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected * pop.scaling.factor) , .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(P_onART = case_when(PLHIV > 0 ~ 100*OnART/PLHIV,
                             PLHIV == 0 ~ 0)) %>% 
  group_by(Year) %>% 
  summarize(P_onART_HIVM1599_M_sd = sd(P_onART), 
            P_onART_HIVM1599_M = mean(P_onART), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_HIVM1599_95LL = lower_ci(P_onART_HIVM1599_M, P_onART_HIVM1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_HIVM1599_95UL = upper_ci(P_onART_HIVM1599_M, P_onART_HIVM1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_onART_HIVM1599_M_sd)

# Percent of HIV positive Female adults on ART, age 15-99
# P_onART_HIVF1599_M
p2 <- sim.results.base %>% 
  filter(Gender == 1, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(OnART = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected * pop.scaling.factor) , .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(P_onART = case_when(PLHIV > 0 ~ 100* OnART/PLHIV,
                             PLHIV == 0 ~ 0)) %>%
  group_by(Year) %>% 
  summarize(P_onART_HIVF1599_M_sd = sd(P_onART), 
            P_onART_HIVF1599_M = mean(P_onART), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_HIVF1599_95LL = lower_ci(P_onART_HIVF1599_M, P_onART_HIVF1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_HIVF1599_95UL = upper_ci(P_onART_HIVF1599_M, P_onART_HIVF1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  )%>% 
  select(-P_onART_HIVF1599_M_sd)

# Percent HIV positive females 15-24 on ART
# P_onART_HIVF1524_M
p3 <- sim.results.base %>% 
  filter(Gender == 1, Age >=15, Age <25) %>% 
  group_by(Year, sim.id) %>% 
  summarize(OnART = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected * pop.scaling.factor) , .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(P_onART = case_when(PLHIV > 0 ~ 100* OnART/PLHIV,
                             PLHIV == 0 ~ 0)) %>%
  group_by(Year) %>% 
  summarize(P_onART_HIVF1524_M = mean(P_onART), 
            .groups = 'keep') %>% 
  ungroup()

# percent hiv positive individuals 15-24 on ART
# P_onART_HIVA1524_M
p4 <- sim.results.base %>% 
  filter(Age >=15, Age <25) %>% 
  group_by(Year, sim.id) %>% 
  summarize(OnART = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected * pop.scaling.factor) , .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(P_onART = case_when(PLHIV > 0 ~ 100* OnART/PLHIV,
                             PLHIV == 0 ~ 0)) %>%
  group_by(Year) %>% 
  summarize(P_onART_HIVA1524_M = mean(P_onART), 
            .groups = 'keep') %>% 
  ungroup()

# percent hiv positive adults on ART
# P_onART_HIVA1599_M
p5 <- sim.results.base %>% 
  filter(Age >=15, Age <25) %>% 
  group_by(Year, sim.id) %>% 
  summarize(OnART = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected * pop.scaling.factor) , .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(P_onART = case_when(PLHIV > 0 ~ 100* OnART/PLHIV,
                             PLHIV == 0 ~ 0)) %>%
  group_by(Year) %>% 
  summarize(P_onART_HIVA1599_M_sd = sd(P_onART), 
            P_onART_HIVA1599_M = mean(P_onART), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_HIVA1599_95LL = lower_ci(P_onART_HIVA1599_M, P_onART_HIVA1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_HIVA1599_95UL = upper_ci(P_onART_HIVA1599_M, P_onART_HIVA1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_onART_HIVA1599_M_sd)

# Percent HIV positive children on ART
# P_onART_HIVA014_M
p6 <- sim.results.base %>% 
  filter(Age >=15, Age <25) %>% 
  group_by(Year, sim.id) %>% 
  summarize(OnART = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected * pop.scaling.factor) , .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(P_onART = case_when(PLHIV > 0 ~ 100* OnART/PLHIV,
                             PLHIV == 0 ~ 0)) %>%
  group_by(Year) %>% 
  summarize(P_onART_HIVA014_M_sd = sd(P_onART), 
            P_onART_HIVA014_M = mean(P_onART), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    P_onART_HIVA014_95LL = lower_ci(P_onART_HIVA014_M, P_onART_HIVA014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    P_onART_HIVA014_95UL = upper_ci(P_onART_HIVA014_M, P_onART_HIVA014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-P_onART_HIVA014_M_sd)

# Percent of HIV positive FSW ages 15+ who are on ART
# P_onART_HIVFSW1599_M
p7 <- sim.results.base %>% 
  filter(Gender == 1, Age >=15, IP_Key.Risk == "HIGH") %>% 
  group_by(Year, sim.id) %>% 
  summarize(OnART = sum(On_ART * pop.scaling.factor), 
            PLHIV = sum(Infected * pop.scaling.factor) , .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(P_onART = case_when(PLHIV > 0 ~ 100* OnART/PLHIV,
                             PLHIV == 0 ~ 0)) %>%
  group_by(Year) %>% 
  summarize(P_onART_HIVFSW1599_M = mean(P_onART), 
            .groups = 'keep') %>% 
  ungroup()

P_onART.current.base <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  merge(p6, by = 'Year') %>%
  merge(p7, by = 'Year') %>%
  mutate(Year = floor(Year)) 

```

## Population

### PrEP Scenario
```{r}
# NAlive_A1599_M
p1 <- sim.results.prep %>% 
  filter(Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_A1599_M_sd = sd(pop), 
            NAlive_A1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_A01599_95LL = lower_ci(NAlive_A1599_M, NAlive_A1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_A01599_95UL = upper_ci(NAlive_A1599_M, NAlive_A1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_A1599_M_sd)

# NAlive_A1549_M
p2 <- sim.results.prep %>% 
  filter(Age >=15, Age < 50) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_A1549_M_sd = sd(pop), 
            NAlive_A1549_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_A01549_95LL = lower_ci(NAlive_A1549_M, NAlive_A1549_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_A01549_95UL = upper_ci(NAlive_A1549_M, NAlive_A1549_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_A1549_M_sd)

# NAlive_M1599_M
p3 <- sim.results.prep %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_M1599_M_sd = sd(pop), 
            NAlive_M1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_M1599_95LL = lower_ci(NAlive_M1599_M, NAlive_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_M1599_95UL = upper_ci(NAlive_M1599_M, NAlive_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_M1599_M_sd)

# NAlive_F1599_M
p4 <- sim.results.prep %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_F1599_M_sd = sd(pop), 
            NAlive_F1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_F1599_95LL = lower_ci(NAlive_F1599_M, NAlive_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_F1599_95UL = upper_ci(NAlive_F1599_M, NAlive_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_F1599_M_sd)

# NAlive_A014_M
p5 <- sim.results.prep %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_A014_M_sd = sd(pop), 
            NAlive_A014_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_A014_95LL = lower_ci(NAlive_A014_M, NAlive_A014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_A014_95UL = upper_ci(NAlive_A014_M, NAlive_A014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_A014_M_sd)

# NAlive_A099_M
p6 <- sim.results.prep %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_A099_M_sd = sd(pop), 
            NAlive_A099_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_A099_95LL = lower_ci(NAlive_A099_M, NAlive_A099_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_A099_95UL = upper_ci(NAlive_A099_M, NAlive_A099_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_A099_M_sd)

# NAlive_FSW1599_M
p7 <- sim.results.prep %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_FSW1599_M_sd = sd(pop), 
            NAlive_FSW1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_A099_95LL = lower_ci(NAlive_FSW1599_M, NAlive_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_A099_95UL = upper_ci(NAlive_FSW1599_M, NAlive_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_FSW1599_M_sd)

NAlive.prep <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  merge(p6, by = 'Year') %>%
  merge(p7, by = 'Year') %>% 
  mutate(Year = floor(Year)) 
```

### Essential Scenario

```{r}
# NAlive_A1599_M
p1 <- sim.results.base %>% 
  filter(Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_A1599_M_sd = sd(pop), 
            NAlive_A1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_A01599_95LL = lower_ci(NAlive_A1599_M, NAlive_A1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_A01599_95UL = upper_ci(NAlive_A1599_M, NAlive_A1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_A1599_M_sd)

# NAlive_A1549_M
p2 <- sim.results.base %>% 
  filter(Age >=15, Age < 50) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_A1549_M_sd = sd(pop), 
            NAlive_A1549_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_A01549_95LL = lower_ci(NAlive_A1549_M, NAlive_A1549_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_A01549_95UL = upper_ci(NAlive_A1549_M, NAlive_A1549_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_A1549_M_sd)

# NAlive_M1599_M
p3 <- sim.results.base %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_M1599_M_sd = sd(pop), 
            NAlive_M1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_M1599_95LL = lower_ci(NAlive_M1599_M, NAlive_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_M1599_95UL = upper_ci(NAlive_M1599_M, NAlive_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_M1599_M_sd)

# NAlive_F1599_M
p4 <- sim.results.base %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_F1599_M_sd = sd(pop), 
            NAlive_F1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_F1599_95LL = lower_ci(NAlive_F1599_M, NAlive_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_F1599_95UL = upper_ci(NAlive_F1599_M, NAlive_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_F1599_M_sd)

# NAlive_A014_M
p5 <- sim.results.base %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_A014_M_sd = sd(pop), 
            NAlive_A014_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_A014_95LL = lower_ci(NAlive_A014_M, NAlive_A014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_A014_95UL = upper_ci(NAlive_A014_M, NAlive_A014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_A014_M_sd)

# NAlive_A099_M
p6 <- sim.results.base %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_A099_M_sd = sd(pop), 
            NAlive_A099_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_A099_95LL = lower_ci(NAlive_A099_M, NAlive_A099_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_A099_95UL = upper_ci(NAlive_A099_M, NAlive_A099_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_A099_M_sd)

# NAlive_FSW1599_M
p7 <- sim.results.base %>% 
  filter(Gender == 0, Age >=15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NAlive_FSW1599_M_sd = sd(pop), 
            NAlive_FSW1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NAlive_A099_95LL = lower_ci(NAlive_FSW1599_M, NAlive_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NAlive_A099_95UL = upper_ci(NAlive_FSW1599_M, NAlive_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NAlive_FSW1599_M_sd)

NAlive.base <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  merge(p6, by = 'Year') %>%
  merge(p7, by = 'Year') %>%
  mutate(Year = floor(Year)) 
```

## PLHIV

### PrEP Scenario
```{r}
# NHIV_M1599_M
p1 <- sim.results.prep %>% 
  filter(Age >=15, Gender == 0) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_M1599_M_sd = sd(pop), 
            NHIV_M1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIV_M1599_95LL = lower_ci(NHIV_M1599_M, NHIV_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIV_M1599_95UL = upper_ci(NHIV_M1599_M, NHIV_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIV_M1599_M_sd)

# NHIV_F1599_M
p2 <- sim.results.prep %>% 
  filter(Age >=15, Gender == 1) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_F1599_M_sd = sd(pop), 
            NHIV_F1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIV_F1599_95LL = lower_ci(NHIV_F1599_M, NHIV_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIV_F1599_95UL = upper_ci(NHIV_F1599_M, NHIV_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIV_F1599_M_sd)

# NHIV_A014_M
p3 <- sim.results.prep %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_M_sd = sd(pop), 
            NHIV_A014_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIV_A014_95LL = lower_ci(NHIV_A014_M, NHIV_A014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIV_A014_95UL = upper_ci(NHIV_A014_M, NHIV_A014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIV_A014_M_sd)

# NHIV_FSW1599_M
p4 <- sim.results.prep %>% 
  filter(Gender == 1, Age >=15, IP_Key.Risk == "HIGH") %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_FSW1599_M_sd = sd(pop), 
            NHIV_FSW1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIV_FSW1599_LL = lower_ci(NHIV_FSW1599_M, NHIV_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIV_FSW1599_UL = upper_ci(NHIV_FSW1599_M, NHIV_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIV_FSW1599_M_sd)

NHIV.prep <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  mutate(Year = floor(Year)) 
```

### Essential Scenario
```{r}
# NHIV_M1599_M
p1 <- sim.results.base %>% 
  filter(Age >=15, Gender == 0) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_M1599_M_sd = sd(pop), 
            NHIV_M1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIV_M1599_95LL = lower_ci(NHIV_M1599_M, NHIV_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIV_M1599_95UL = upper_ci(NHIV_M1599_M, NHIV_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIV_M1599_M_sd)

# NHIV_F1599_M
p2 <- sim.results.base %>% 
  filter(Age >=15, Gender == 1) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_F1599_M_sd = sd(pop), 
            NHIV_F1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIV_F1599_95LL = lower_ci(NHIV_F1599_M, NHIV_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIV_F1599_95UL = upper_ci(NHIV_F1599_M, NHIV_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIV_F1599_M_sd)

# NHIV_A014_M
p3 <- sim.results.base %>% 
  filter(Age < 15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_A014_M_sd = sd(pop), 
            NHIV_A014_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIV_A014_95LL = lower_ci(NHIV_A014_M, NHIV_A014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIV_A014_95UL = upper_ci(NHIV_A014_M, NHIV_A014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIV_A014_M_sd)

# NHIV_FSW1599_M
p4 <- sim.results.base %>% 
  filter(Gender == 1, Age >=15, IP_Key.Risk == "HIGH") %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(NHIV_FSW1599_M_sd = sd(pop), 
            NHIV_FSW1599_M = mean(pop), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    NHIV_FSW1599_LL = lower_ci(NHIV_FSW1599_M, NHIV_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    NHIV_FSW1599_UL = upper_ci(NHIV_FSW1599_M, NHIV_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-NHIV_FSW1599_M_sd)

NHIV.base <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  mutate(Year = floor(Year)) 
```


## Prevalence

### PrEP Scenario
```{r}
# HIVprev_M1549_M
p1 <- sim.results.prep %>% 
  filter(Age >=15, Age<50, Gender == 0) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(pop > 0 ~ PLHIV/pop,
                          pop == 0 ~ 0)) %>% 
  group_by(Year) %>% 
  summarize(HIVprev_M1549_M_sd = sd(prev), 
            HIVprev_M1549_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVprev_M1549_95LL = lower_ci(HIVprev_M1549_M, HIVprev_M1549_M_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVprev_M1549_95UL = upper_ci(HIVprev_M1549_M, HIVprev_M1549_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-HIVprev_M1549_M_sd)

# HIVprev_F1549_M
p2 <- sim.results.prep %>% 
  filter(Age >=15, Age<50, Gender == 1) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(pop > 0 ~ PLHIV/pop,
                          pop == 0 ~ 0)) %>% 
  group_by(Year) %>% 
  summarize(HIVprev_F1549_M_sd = sd(prev), 
            HIVprev_F1549_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVprev_F1549_95LL = lower_ci(HIVprev_F1549_M, HIVprev_F1549_M_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVprev_F1549_95UL = upper_ci(HIVprev_F1549_M, HIVprev_F1549_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-HIVprev_F1549_M_sd)

# HIVprev_A1549_M
p3 <- sim.results.prep %>% 
  filter(Age >=15, Age<50) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(pop > 0 ~ PLHIV/pop,
                          pop == 0 ~ 0)) %>% 
  group_by(Year) %>% 
  summarize(HIVprev_A1549_M_sd = sd(prev), 
            HIVprev_A1549_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVprev_A1549_95LL = lower_ci(HIVprev_A1549_M, HIVprev_A1549_M_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVprev_A1549_95UL = upper_ci(HIVprev_A1549_M, HIVprev_A1549_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-HIVprev_A1549_M_sd)

# HIVprev_F1524_M
p4 <- sim.results.prep %>% 
  filter(Age >=15, Age<25, Gender == 1) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(pop > 0 ~ PLHIV/pop,
                          pop == 0 ~ 0)) %>% 
  group_by(Year) %>% 
  summarize(HIVprev_F1524_M_sd = sd(prev), 
            HIVprev_F1524_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVprev_F1524_95LL = lower_ci(HIVprev_F1524_M, HIVprev_F1524_M_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVprev_F1524_95UL = upper_ci(HIVprev_F1524_M, HIVprev_F1524_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-HIVprev_F1524_M_sd)

# HIVprev_FSW1599_M
p5 <- sim.results.prep %>% 
  filter(Age >=15, Gender == 1, IP_Key.Risk == "HIGH") %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(pop > 0 ~ PLHIV/pop,
                          pop == 0 ~ 0)) %>% 
  group_by(Year) %>% 
  summarize(HIVprev_FSW1599_M_sd = sd(prev), 
            HIVprev_FSW1599_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVprev_FSW1599_95LL = lower_ci(HIVprev_FSW1599_M, HIVprev_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVprev_FSW1599_95UL = upper_ci(HIVprev_FSW1599_M, HIVprev_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-HIVprev_FSW1599_M_sd)

HIVprev.prep <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  mutate(Year = floor(Year)) 
```

### Essential Scenario
```{r}
# HIVprev_M1549_M
p1 <- sim.results.base %>% 
  filter(Age >=15, Age<50, Gender == 0) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(pop > 0 ~ PLHIV/pop,
                          pop == 0 ~ 0)) %>% 
  group_by(Year) %>% 
  summarize(HIVprev_M1549_M_sd = sd(prev), 
            HIVprev_M1549_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVprev_M1549_95LL = lower_ci(HIVprev_M1549_M, HIVprev_M1549_M_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVprev_M1549_95UL = upper_ci(HIVprev_M1549_M, HIVprev_M1549_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-HIVprev_M1549_M_sd)

# HIVprev_F1549_M
p2 <- sim.results.base %>% 
  filter(Age >=15, Age<50, Gender == 1) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(pop > 0 ~ PLHIV/pop,
                          pop == 0 ~ 0)) %>% 
  group_by(Year) %>% 
  summarize(HIVprev_F1549_M_sd = sd(prev), 
            HIVprev_F1549_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVprev_F1549_95LL = lower_ci(HIVprev_F1549_M, HIVprev_F1549_M_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVprev_F1549_95UL = upper_ci(HIVprev_F1549_M, HIVprev_F1549_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-HIVprev_F1549_M_sd)

# HIVprev_A1549_M
p3 <- sim.results.base %>% 
  filter(Age >=15, Age<50) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(pop > 0 ~ PLHIV/pop,
                          pop == 0 ~ 0)) %>% 
  group_by(Year) %>% 
  summarize(HIVprev_A1549_M_sd = sd(prev), 
            HIVprev_A1549_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVprev_A1549_95LL = lower_ci(HIVprev_A1549_M, HIVprev_A1549_M_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVprev_A1549_95UL = upper_ci(HIVprev_A1549_M, HIVprev_A1549_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-HIVprev_A1549_M_sd)

# HIVprev_F1524_M
p4 <- sim.results.base %>% 
  filter(Age >=15, Age<25, Gender == 1) %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(pop > 0 ~ PLHIV/pop,
                          pop == 0 ~ 0)) %>% 
  group_by(Year) %>% 
  summarize(HIVprev_F1524_M_sd = sd(prev), 
            HIVprev_F1524_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVprev_F1524_95LL = lower_ci(HIVprev_F1524_M, HIVprev_F1524_M_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVprev_F1524_95UL = upper_ci(HIVprev_F1524_M, HIVprev_F1524_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-HIVprev_F1524_M_sd)

# HIVprev_FSW1599_M
p5 <- sim.results.base %>% 
  filter(Age >=15, Gender == 1, IP_Key.Risk == "HIGH") %>% 
  group_by(Year, sim.id) %>% 
  summarize(pop = sum(Population * pop.scaling.factor), 
            PLHIV = sum(Infected*pop.scaling.factor), .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(prev = case_when(pop > 0 ~ PLHIV/pop,
                          pop == 0 ~ 0)) %>% 
  group_by(Year) %>% 
  summarize(HIVprev_FSW1599_M_sd = sd(prev), 
            HIVprev_FSW1599_M = mean(prev), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    HIVprev_FSW1599_95LL = lower_ci(HIVprev_FSW1599_M, HIVprev_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    HIVprev_FSW1599_95UL = upper_ci(HIVprev_FSW1599_M, HIVprev_FSW1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-HIVprev_FSW1599_M_sd)

HIVprev.base <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  merge(p5, by = 'Year') %>%
  mutate(Year = floor(Year)) 
```

## Deaths

### PrEP Scenario
```{r}
# TOTDeaths_M1599_M
p1 <- sim.results.prep %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >=15, Gender == 0) %>% 
  group_by(Year, sim.id) %>% 
  summarize(TOTDeaths_M1599_M = sum(Died * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(TOTDeaths_M1599_M_sd = sd(TOTDeaths_M1599_M), 
            TOTDeaths_M1599_M = mean(TOTDeaths_M1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    TOTDeaths_M1599_95LL = lower_ci(TOTDeaths_M1599_M, TOTDeaths_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    TOTDeaths_M1599_95UL = upper_ci(TOTDeaths_M1599_M, TOTDeaths_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-TOTDeaths_M1599_M_sd)

# TOTDeaths_F1599_M
p2 <- sim.results.prep %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >=15, Gender == 1) %>% 
  group_by(Year, sim.id) %>% 
  summarize(TOTDeaths_F1599_M = sum(Died * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(TOTDeaths_F1599_M_sd = sd(TOTDeaths_F1599_M), 
            TOTDeaths_F1599_M = mean(TOTDeaths_F1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    TOTDeaths_F1599_95LL = lower_ci(TOTDeaths_F1599_M, TOTDeaths_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    TOTDeaths_F1599_95UL = upper_ci(TOTDeaths_F1599_M, TOTDeaths_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-TOTDeaths_F1599_M_sd)

# TOTDeaths_A014_M
p3 <- sim.results.prep %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age <15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(TOTDeaths_A014_M = sum(Died * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(TOTDeaths_A014_M_sd = sd(TOTDeaths_A014_M), 
            TOTDeaths_A014_M = mean(TOTDeaths_A014_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    TOTDeaths_A014_95LL = lower_ci(TOTDeaths_A014_M, TOTDeaths_A014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    TOTDeaths_A014_95UL = upper_ci(TOTDeaths_A014_M, TOTDeaths_A014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-TOTDeaths_A014_M_sd)

# TOTDeaths_A1599_M
p4 <- sim.results.prep %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age <15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(TOTDeaths_A1599_M = sum(Died * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(TOTDeaths_A1599_M_sd = sd(TOTDeaths_A1599_M), 
            TOTDeaths_A1599_M = mean(TOTDeaths_A1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    TOTDeaths_A1599_95LL = lower_ci(TOTDeaths_A1599_M, TOTDeaths_A1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    TOTDeaths_A1599_95UL = upper_ci(TOTDeaths_A1599_M, TOTDeaths_A1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-TOTDeaths_A1599_M_sd)


TOTDeaths.prep <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  mutate(Year = floor(Year)) 
```


### Essential Scenario
```{r}
# TOTDeaths_M1599_M
p1 <- sim.results.base %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >=15, Gender == 0) %>% 
  group_by(Year, sim.id) %>% 
  summarize(TOTDeaths_M1599_M = sum(Died * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(TOTDeaths_M1599_M_sd = sd(TOTDeaths_M1599_M), 
            TOTDeaths_M1599_M = mean(TOTDeaths_M1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    TOTDeaths_M1599_95LL = lower_ci(TOTDeaths_M1599_M, TOTDeaths_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    TOTDeaths_M1599_95UL = upper_ci(TOTDeaths_M1599_M, TOTDeaths_M1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-TOTDeaths_M1599_M_sd)

# TOTDeaths_F1599_M
p2 <- sim.results.base %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age >=15, Gender == 1) %>% 
  group_by(Year, sim.id) %>% 
  summarize(TOTDeaths_F1599_M = sum(Died * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(TOTDeaths_F1599_M_sd = sd(TOTDeaths_F1599_M), 
            TOTDeaths_F1599_M = mean(TOTDeaths_F1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    TOTDeaths_F1599_95LL = lower_ci(TOTDeaths_F1599_M, TOTDeaths_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    TOTDeaths_F1599_95UL = upper_ci(TOTDeaths_F1599_M, TOTDeaths_F1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-TOTDeaths_F1599_M_sd)

# TOTDeaths_A014_M
p3 <- sim.results.base %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age <15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(TOTDeaths_A014_M = sum(Died * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(TOTDeaths_A014_M_sd = sd(TOTDeaths_A014_M), 
            TOTDeaths_A014_M = mean(TOTDeaths_A014_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    TOTDeaths_A014_95LL = lower_ci(TOTDeaths_A014_M, TOTDeaths_A014_M_sd/sqrt(nruns), nruns, conf_level = .95),
    TOTDeaths_A014_95UL = upper_ci(TOTDeaths_A014_M, TOTDeaths_A014_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-TOTDeaths_A014_M_sd)

# TOTDeaths_A1599_M
p4 <- sim.results.base %>% 
  mutate(Year = ceiling(Year)) %>% 
  filter(Age <15) %>% 
  group_by(Year, sim.id) %>% 
  summarize(TOTDeaths_A1599_M = sum(Died * pop.scaling.factor), .groups = 'keep') %>% 
  group_by(Year) %>% 
  summarize(TOTDeaths_A1599_M_sd = sd(TOTDeaths_A1599_M), 
            TOTDeaths_A1599_M = mean(TOTDeaths_A1599_M), 
            .groups = 'keep') %>% 
  ungroup() %>% 
  mutate(
    TOTDeaths_A1599_95LL = lower_ci(TOTDeaths_A1599_M, TOTDeaths_A1599_M_sd/sqrt(nruns), nruns, conf_level = .95),
    TOTDeaths_A1599_95UL = upper_ci(TOTDeaths_A1599_M, TOTDeaths_A1599_M_sd/sqrt(nruns), nruns, conf_level = .95)
  ) %>% 
  select(-TOTDeaths_A1599_M_sd)


TOTDeaths.base <- merge(p1, p2, by = 'Year') %>% 
  merge(p3, by = 'Year') %>% 
  merge(p4, by = 'Year') %>%
  mutate(Year = floor(Year)) 
```

## Testing

## PrEP

Unfortunately this part isn't ready yet

# Write out results to form

## PrEP Scenario
```{r}
analysis.path <- "/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/Analysis/"

(inc.prep.summary)[c(-3, -7, -11, -15, -19)] %>% filter(Year >= 2022) %>% 
  merge(ylls.current.prep  %>% filter(Year >= 2022),
      by = "Year") %>% 
  merge(prep.prep.summary  %>% filter(Year >= 2022),
        by = "Year") %>% 
  merge(TOTDeaths.prep %>% filter(Year >= 2022),
        by = "Year") %>%  
  write_csv(file = paste0(analysis.path, 'Template_FLOW_prep_scenario.csv'))


ylds.current.prep %>% filter(Year >= 2023) %>% 
  merge(NAlive.prep %>% filter(Year >= 2023),
        by = "Year") %>% 
  merge(NHIV.prep %>% filter(Year >= 2023),
        by = "Year") %>% 
  merge(HIVprev.prep %>% filter(Year >= 2023),
        by = "Year") %>% 
  merge(NOnART.current.prep %>% filter(Year >= 2023),
      by = "Year") %>% 
  merge(P_onART.current.prep %>% filter(Year >= 2023),
      by = "Year") %>% 
  write_csv(file = paste0(analysis.path, 'Template_STOCK_prep_scenario.csv'))
```

## Essential Scenario
```{r}
analysis.path <- "/gpfs/data/bershteynlab/EMOD/citrod01/ZWE_calib_20220627/Analysis/"

(inc.base.summary)[c(-3, -7, -11, -15, -19)] %>% filter(Year >= 2022) %>% 
  merge(ylls.current.base  %>% filter(Year >= 2022),
      by = "Year") %>% 
  merge(prep.base.summary  %>% filter(Year >= 2022),
        by = "Year") %>% 
    merge(TOTDeaths.base %>% filter(Year >= 2022),
        by = "Year") %>%  
  write_csv(file = paste0(analysis.path, 'Template_FLOW_essential_scenario.csv'))

ylds.current.base %>% filter(Year >= 2023) %>% 
    merge(NAlive.base %>% filter(Year >= 2023),
        by = "Year") %>% 
  merge(NHIV.base %>% filter(Year >= 2023),
        by = "Year") %>% 
  merge(HIVprev.base %>% filter(Year >= 2023),
        by = "Year") %>% 
  merge(NOnART.current.base %>% filter(Year >= 2023),
      by = "Year") %>% 
  merge(P_onART.current.base %>% filter(Year >= 2023),
      by = "Year") %>% 
  write_csv(file = paste0(analysis.path, 'Template_STOCK_essential_scenario.csv'))
```

